
\documentclass[char]{Kos}
\begin{document}
\name{\cArmsDealer{}}

Born February 16, in the year 268.

War is good for business. That's what everyone says, at least. And you suspect that the old adage might well be true. But you'd like to put it more precisely: war is good for \emph{your} business. That is to say, your business happens to be the sale of new and deadly weapons to the highest bidder. And if you want to get Etruria and Scythia to pay a premium for your newest innovations - well, then war could be quite profitable indeed. Now you just need to make sure a devastating conflict ensues - and since you've been invited to the royal wedding, alongside the rulers and heirs of both factions, it seems like an excellent time to manipulate the situation and make sure things go your way.

You've been attached to the royal court of Scythia for years now, trading military secrets with incautious generals and making sure the royal guard stays well-supplied and heavily armed. During this time, you've managed to develop a contact at the very highest levels of the Scythian government: you've cultivated quite a friendship with no less than \cScythiaQueen{\Monarch} \cScythiaQueen{} herself. You first bonded over your shared hatred for Etruria - yours has been feigned from a young age, ever since you realized that nothing sells weapons more convincingly than patriotism. But you'll never share that particular revelation with \cScythiaQueen{}, since \cScythiaQueen{\their} loathing for that rival nation appears to be frighteningly, sometimes terrifyingly, real.

Thankfully, you've got evidence to back up your claims. Years back, when the Etruscans razed the border town of Achillea, three of your cousins were killed by \cEtruriaKing{\Monarch} \cEtruriaKing{}'s troops. They were second cousins by marriage, and you never really liked them anyways, but that's not the point - and you certainly don't mention that last part when you're speaking to the \cScythiaQueen{\Monarch}. Instead, you let a couple of tears fall - a wonderful talent, the ability to cry at the drop of a hat - and \cScythiaQueen{}'s ready to put reason aside and let \cScythiaQueen{\their} wrath take over.

\cScythiaQueen{}, you suppose, has reason enough to despise Etruria. First they killed \cScythiaQueen{\their} childhood friends when they burned down Achillea, then they took \cScythiaQueen{\their} own daughter from \cScythiaQueen{\them} in the night. \cScythiaQueen{\They}'s lost a lot. But try as you might, it's hard for you to imagine the white-hot emotions coursing through \cScythiaQueen{\their} veins. Profit and opportunity speak to you most dearly, not pathetic sentiment - but if you can use the \cScythiaQueen{\Monarch}'s emotions to sway \cScythiaQueen{\them} towards war, then you've no compunctions about doing so.

Unfortunately, not everyone agrees with you on that particular point. Also attending the wedding is the Etrsucan merchant \cMerchant{}, a purveyor of luxury goods and a pacifistic coward. Not that \cMerchant{}'s got any more moral compunctions than you do - as a matter of fact, \cMerchant{\they}'s a vile and avaricious termite of a \cMerchant{\human}. \cMerchant{\They} craves profit even more shamelessly than you - and \cMerchant{\they}'s not got an honest bone in \cMerchant{\their} body. \cMerchant{\They}'s a conniver, a deceiver, a forger, a manipulative scorpion who will stop at nothing to quash the fledgling conflict between the Sabine factions and peddle \cMerchant{\their} posh snake-oil trinkets to the rich and stupid nobles of both nations. You've encountered the \cMerchant{\human} too many times before at Assyrian trade conferences. Even worse, \cMerchant{\they}'s gotten the better of you as often as not, ``persuading'' the nobles in attendance to tweak the import tariffs and trade laws in \cMerchant{\their} favor. This is embarrassing, it's humiliating, and you'll never admit it to your customers. It's surprisingly difficult for you to damage \cMerchant{\their} credibility - you've tried accusing \cMerchant{\them} of being a dirty money-grubbing piece of slime who cares about nothing but profit, but \cMerchant{\they} always manages to twist your words around and fire them back at you. No good, no good at all. What's more, every time you attend a trade summit or Assyrian bazaar, you find yourself seated across the table from \cMerchant{\them} in a game of Bluffmaster - you're certain the bastard cheats, because you recall losing to \cMerchant{\them} as often as you won. This simply will not do. You'd like nothing more than to clean \cMerchant{} out at the gambling tables and show \cMerchant{\them} up for the nefarious trickster that \cMerchant{\they} is.

This time, though, \cMerchant{}'s overstepped \cMerchant{\their} bounds, and if you play your cards right, you might well be able to destroy \cMerchant{\their} reputation permanently. The fool's been bragging to anyone who will listen that \cMerchant{\they}'s come across an ancient relic - the legendary Diadem of the Sabines. Thankfully, you've done your history research. You've always loved history, ever since you realized that no one knows more about how to start a war than the historians. Anyways, an obscure source you once read, deep in the Scythian archives, mentioned that the Diadem was lost on the island of Cos, a site that \cMerchant{}'s never visited - so it's inconceivable that \cMerchant{\they} could possess it. Therefore, you've concluded, \cMerchant{}'s version must be a fake. 

The tricky part will be proving it. \cMerchant{}'s not only a nefarious forger, but also a talented one - and you've no doubt that \cMerchant{\they}'s imitated the Diadem as closely as \cMerchant{\they} can. So there's only one way to show the assembled royals that \cMerchant{}'s a liar, and \cMerchant{\their} wares are spurious: dig up the real Diadem from its long-forgotten hiding-place on Cos and show it to the crowd. Thankfully, you've got some leads in this regard - your preliminary research suggests that it disappeared when Smaragdos's ship wrecked in a storm and stranded her on Cos. The ancient queen, plagued by some wasting disease, managed to conceal the Diadem before she died. She left behind a trail of golden sigils, intended to lead the worthy to the Diadem's hiding place and conceal it from the prying eyes of the common rabble.

You've also got no love lost for \cEtruriaKing{}, Etruria's cruel genius of a \cEtruriaKing{\monarch}. You know \cEtruriaKing{\they}'s brilliantly intelligent, but also suspect that \cEtruriaKing{\they} may have intercepted one of your recent arms shipments containing a powerful but unpredictable new explosive - the bireme conveying it disappeared without a trace several weeks prior. You think Etruria's planning to use the weapon to attack Scythia and catch \cScythiaKing{} by surprise. Now, that's not necessarily a bad thing - after all, it could prove profitable in the long run - but you'd very much like to figure out exactly who's got their hands on your weaponry and why they plan on using it. After all, if there's going to be chaos, you want to know what's going to happen in advance so you can use it to your advantage. Besides, that's your merchandise they took. You'd very much like to get it back.

On the other hand, there's also a chance for real personal profit here - as there nearly always is at such gatherings. Explosives are all well and good for bulk sales, but you would be well served to invest in something a little more subtle. Your contacts within Scythia's order of Soulblades have informed you that the Blackguards, an ancient order of Etruscan assassins, might be targeting the wedding for their own nefarious purposes. You've interacted with the defunct Assyrian branch of the order before, and they're quite a rogues' gallery of nefarious individuals. Their presence at the wedding is good news, so long as you can avoid being on the receiving end of a knife in the back yourself - the Blackguards use a variety of esoteric and frighteningly effective poisons to carry out their missions. If you can get your hands on as many samples as possible - at least one of their delivery objects, impregnated with a full dose of poison, or a vial of the poison itself - your organization should be able to replicate them for mass production. You've heard rumors that the Blackguards use ordinary-seeming sewing needles to carry out their hits - perhaps you should start there. If you can figure out who these Blackguards are, you might be able to go a step further - try to get in their good graces without risking your own life in the process. If you open up a line of contact now, you might be able to unearth even more secrets from their alchemists and artificers further down the line.

There's one last obstacle to your ambitions - the meddling Assyrian diplomat, Sirasu Noon. That man has an uncanny talent for sticking his nose where it doesn't belong. Obsessed with peace, he's interfered with your arms deals and carefully-laid plans before - which will just make it more satisfying when you drag the nations into war \emph{right under his nose}.

No question about it, you could walk away from this wedding with full pockets and a smile on your face. All you need to do is outsmart that devil \cMerchant{}, and goad the assembled royals into war and chaos, and the profits are yours for the taking.

\begin{itemz}[Goals]
\item Discredit that self-satisfied toad \cMerchant{} however you can.
\item Provoke \cScythiaQueen{\Monarch} \cScythiaQueen{} and the other Scythian royals into declaring war with Etruria.
\item Find the real Diadem on Cos and use it to prove that \cMerchant{}'s copy is a crude forgery.
\item Get your hands on a sample of Blackguard poison.
\item Figure out what happened to your missing cache of explosives.
\item Prove your mental superiority by demolishing \cMerchant{} utterly at the Bluffmaster table.
\end{itemz}

\begin{contacts}
\contact{\cMerchant{}} An Etruscan luxury merchant and a greedy, money-grubbing piece of slime.
\contact{\cScythiaQueen{}} The revenge-blind \cScythiaQueen{\monarch} of Scythia, and an old friend of yours.
\contact{\cEtruriaKing{}} The Etruscan \cEtruriaKing{\monarch}, a cunning ruler and potential customer who may well have stolen your prototype explosives.
\end{contacts}


\end{document}

