
\documentclass[char]{Kos}
\begin{document}
\name{\cAssassin{}}

Born June 1, in the year 245.

    No wise \cEtruriaKing{\monarch} travels unattended, and \cEtruriaKing{} is no exception. At the subtlest gesture - a shrug, a nod, the twitch of a finger - a wordless, dutiful servant appears behind \cEtruriaKing{\them}, ready and willing to serve. It is for this purpose that the Etruscan court keeps a highly trained and disciplined staff, ready and willing to supply whatever the \cEtruriaKing{\monarch} should require. Though the royal wedding takes place on the remote isle of Cos, \cEtruriaKing{\they} has chosen you, \cEtruriaKing{\their} favorite attendant, to accompany \cEtruriaKing{\them}.

    But you were trained to be far more than a mere attendant. That's nothing more than a cover story, meticulously rehearsed and years in the making. You are one of the most proficient of Etruria's nefarious and secretive order of Blackguards, and \cEtruriaKing{\Monarch} \cEtruriaKing{}' most reliable agent. In all of Etruria, you answer to only two people: the White Rose, the elusive commander of the Blackguards, and the \cEtruriaKing{\Monarch} himself. To maintain the utmost degree of secrecy, even the \cEtruriaKing{\Monarch} has no idea who you really are: \cEtruriaKing{\they} sends \cEtruriaKing{\their} commands to the White Rose via a hidden communications device, and the White Rose relays those orders to you.

    Until recently, you didn't even answer to the two of them. You were happily retired, ready to while out the rest of your days at a Mediterranean estate. But you kept up with Etruria's political affairs, just to while away the time - and, let's face it, the next generation of Blackguards has been making a gods-awful mess of things. After reading reports of debacle after debacle, you lost all faith in those incompetents. So when the White Rose offered you an opportunity to accompany \cEtruriaKing{}' retinue to the wedding, and deliver a royal death sentence to not one but two unsuspecting targets, you knew you had to accept. No more shame would be visited on your ancient and dreaded order. You will make sure of that. Though the years have begun to weigh on you, few are more skilled with the arts of poison and subterfuge than you. Soon those who have been marked for death will feel the sting of a deadly needle or the sizzle of poisoned fabric against their vulnerable skin.

    Yet, if truth be told, the nature of the assassinations you have been tasked with is - peculiar, to say the least. The \cEtruriaKing{\monarch}, loveless and calculating at the best of times, nevertheless has brought \cEtruriaKing{\their} two heirs with \cEtruriaKing{\them} to the festivities - \cEtruriaKing{\their} eldest, crown \cGroom{\Prince} \cGroom{}, the intended groom and perhaps the best chance for peace between Etruria and Scythia, and \cEtruriaKing{\their} younger \cPoet{\offspring} \cPoet{}, an impetuous rake more given to poetry and drink than any semblance of royal dignity. You have been tasked with killing both of these Etruscan heirs before sunset begins today, and the White Rose has assured you that these commands come from the \cEtruriaKing{\monarch} himself. It seems strange, to say the least, that the aging \cEtruriaKing{} would be so keen to sever \cEtruriaKing{\their} own bloodline at the roots. Perhaps, sick of \cGroom{}'s lukewarm attitude towards the throne, and disgusted with \cPoet{}'s improprieties, \cEtruriaKing{\they} decided that neither of them were worthy heirs. Or perhaps the prophesied conflict looming on the horizon appeals more to \cEtruriaKing{} than another generation of stagnant and nervous peace. It doesn't matter to you. After all, who are you to gainsay a \cEtruriaKing{\monarch}? You'll do your job, and do it cleanly and secretly, arousing no suspicion. 

    Not that you've any love for \cEtruriaKing{} himself. You remember \cEtruriaKing{\their} father, Hyperion, with nothing but bitterness, and long for the good old days when women of pure Etruscan blood sat upon the throne. But it's the worst form of dishonor for a Blackguard to act against their rightful ruler, no matter what their personal feelings might be. You're supposed to simply swallow your pride, and provide a shining example to the newer Blackguards of what it means to be a true professional. But is \cEtruriaKing{\Monarch} \cEtruriaKing{} your \emph{rightful} ruler? Certainly \cEtruriaKing{\their} hands are stained with the blood of the ancient queens, who proved more noble than \cEtruriaKing{\they} and the rest of the Coroni have ever been. Rumor has it that despite the best efforts of the Coronus dynasty, at least one full-blooded Etruscan royal survived the coup. Perhaps some day the stain of the Coroni will be washed from these lands, and you can kneel before a true Etruscan queen once more. Perhaps some day.

The memory of those bloody days still haunts you - as does your own role in the massacre. Thoughtlessly following the orders of a past White Rose, now long-dead, you betrayed the dynasty you once swore to serve. It was at your hands that the rightful queen of Etruria met her end, mortally wounded as she tried desperately to escape the bloodshed. That act has weighed on you ever since. Only when you dedicate yourself to the orders before you, focusing stubbornly on the details of your job, can you forget the blood that stains your hands. You tell yourself that you proved your loyalty to the Blackguards that day - but what was that loyalty truly worth, if it meant betraying your rightful sovereign?

    Nor, astonishingly enough, are you the only Blackguard present at the wedding. A secret communique, sent along ancient and half-forgotten channels of communication, reached the White Rose some time ago, announcing that a Blackguard of Assyria would also be present at the ceremony, and willing to assist you if you required it. This is problematic, to say the least: the Assyrian order of Blackguards collapsed long ago, and with no White Rose to lead them, the few members who remain are chaotic and unpredictable loose cannons who make Etruria's assassins seem competent by comparison. You're not sure if seeking out this Blackguard will prove them an ally or a liability - but perhaps you ought to figure out who they are, just to make sure they don't interfere with your plans. But, if you care to find this mysterious assassin, following the ceremonial sign of the Blackguards - the rose - will lead you to them.

    There are also larger fates at stake here. On this wedding rests the question of war or peace. Though you view \cEtruriaKing{\Monarch} \cEtruriaKing{} \cEtruriaKing{\them}self with little more than distrustful contempt, Etruria has always been your home, and you could not bear to see it ravaged by conquest. If war does break out, you would rather see Etruria prevail, even led by \cEtruriaKing{}, than hear the baleful tromp of Scythian boots on Etruscan soil, as the fields lie fallow and the cities burn. Perhaps peace is the safer course - but, if at all possible, you would love to see a war that Etruria can win. 

    And you are not without desires of your own. Long ago, before you were first initiated into the Blackguards, your baby sister Cygna was taken with a terrible wasting illness, the Black Malady that sometimes ravages the lands of the old Sabine Empire. Driven to save her at any cost, your parents had her smuggled into Scythia, hoping that the death-obsessed mystics known as the Soulblades could stave off the ailment that threatened to devour her. You traveled with them, and watched as the Soulblades conjured inky tendrils of darkness from thin air to suffuse Cygna's veins and cloud her eyes - and you were there when she first screamed in agony. The ritual of the Soulblades saved her, true, but at terrible cost - she is trapped in the shell of her own body, unable to speak or move or even scream. But you can see the pain that wracks her every time you look in her eyes. She lives to this day, provided with every luxury you can afford. You have heard tell of an Assyrian alchemist who may be able to reverse the process that trapped Cygna's soul and left her writhing in unspeakable pain and crippling silence - but his price is far higher than you had hoped, and your coffers are nearly empty. Worst of all, he is set to leave Etruria for Assyria this week, and Cygna is too ill to ever travel there. Thus, you must find the money you require immediately, at the wedding, and use it to bring back the Cygna you once knew. Your talent for concealment and deception translates well to the game of Bluffmaster, a game that was once part of your training as a Blackguard. You have brought what little funds you have remaining with you to the wedding - hopefully you can multiply them into a sum great enough to heal your sister. You cannot bear to look your sister in the eye and admit that you failed her once again. You have to save her.

    And, if you should chance upon any Soulblades at the wedding - their vile magic doomed Cygna to a lifetime of despair. No power is worth that risk. No power is worth inflicting that fate on another human being. Any who practice the magic of the Soulblades should be stopped, at any cost. Cygna would desire nothing less.
    
\begin{itemz}[Notes]
  \item You've got one of the Blackguards' greatest tools in your trunk-- a handkerchief that paralyzes anyone who touches it with their bare skin. You also have a needle you can use to dose someone with poison.
    \end{itemz}


\begin{itemz}[Goals]
\item Carry out your orders from the White Rose and assassinate \cGroom{} and \cPoet{} before sunset.
\item Use whatever means you can to undermine the authority of \cEtruriaKing{\Monarch} \cEtruriaKing{}.
\item Root out evidence of Soulblade magic and quash their reckless, destructive rituals.
\item Make contact with the Blackguard among the Assyrian delegation.
\item Leave the wedding with enough money to heal your sister Cygna: 500 gold pieces.
\end{itemz}

\begin{contacts}
\contact{\cEtruriaKing{}} A coldly brilliant monarch, the \cEtruriaKing{\offspring} of the usurper-king Hyperion Coronus.
\contact{\cGroom{}} Your secondary target, the dignified older \cGroom{\offspring} of  \cEtruriaKing{\Monarch} \cEtruriaKing{}.
\contact{\cPoet{}} Your secondary target, the rakish younger \cPoet{\offspring} of  \cEtruriaKing{\Monarch} \cEtruriaKing{}.
\contact{\cMerchant{}} A merchant of luxury goods.
\end{contacts}


\end{document}
