\documentclass[char]{Kos}
\begin{document}
\name{\cButler{}}

Born November 7, in the year 276.

Nobody lives happily ever after, but I swear I'll still try.

I grew up cursed by my own talents. My father was Memnon, one of the celebrated Scythian Soulblades, but he proclaimed at my birth that I had more potential than any other mage, ever. He therefore inducted me into the horrors of life and death magic when I was still a small child, and my earliest memories were filled with the rattling of bells, the murmuring of malevolent ghosts, with black zigzags that stuck to me like bandages on a mummy. The dark magic, whose purpose I still do not understand, nearly drove me to madness, and I fled when I was just nine, running for miles to non-magical relatives on my mother's side. I never returned to Scythia's Soulblade Quarter, which was raided soon afterwards, thanks to the vigilant \cScythiaQueen{\Monarch} \cScythiaQueen{}. It turned out the Soulblades had been breaking the law, using human organs and other unsavory ingredients. Father was jailed for life, and I never saw him again.

Thus, a new chapter began. I dropped out of school at fifteen-- though I still read widely and am hardly ignorant-- with hopes of working in the palace. I was personally interviewed by \cScythiaQueen{\Monarch} \cScythiaQueen{}, and \cScythiaQueen{\they} asked whether I had indeed abandoned the Soulblades, whom \cScythiaQueen{\they} openly opposes; I promised I had left them entirely, and \cScythiaQueen{\they} verified my answer with royal divination magic. Soon afterwards, I began as a server in the dining halls and quickly rose through the ranks to the office of steward, working day and night, performing my duties as diligently and elegantly as possible. I am loyal to Scythia and glad to serve it, and the orderly nature of palace life was a comfort after my chaotic childhood.

But a few years ago, my world was thrown back into disarray. There was a ball at the Scythian palace, in honor of the crown \cBride{\prince} \cBride{}, who had recently returned from law school in Assyria. Before, I thought of \cBride{\them} as a coltish adolescent, but I now saw an angel in white and gold robes, radiant with some inner joy. Enthralled, I continued to watch \cBride{\them}. At first, I could do nothing but admire \cBride{\them}, like a fine statue, for \cBride{\they} seemed too perfect to be real. But I slowly discerned something underneath the brilliance-- anxiety, and a depth of pain-- and I fell in love. 

Loving \cBride{\them} hurts. The more I watched \cBride{\them}, the more I grieved, for \cBride{\they} clearly struggles with great burdens. \cBride{\Their} \cFugitive{\sibling} died, yes, but I can't help feeling that \cBride{}'s suffering from fresher pain as well. Soon afterwards, I was promoted to steward, the top position in the servants' hierarchy, so I had the freedom to move throughout the whole palace at all hours and observe \cBride{\them} more closely. What I found stunned me-- \cBride{\they} was an alcoholic.

I immediately knew I had to help \cBride{\them}. And so, after so many years of shunning Soulblade arts, I returned to magic. Though the Soulblades had never found a cure for alcoholism, I threw my not inconsiderable efforts into the search and, after a few months of experimentation, concocted a partial remedy; while I could not guarantee that \cBride{\they} would be healed, I would at least increase \cBride{\their} chances of recovery. So I slipped the cure into \cBride{\their} soup at dinner, and, from the next day on, \cBride{\they} ceased drinking. I rejoiced, thrilled to have helped \cBride{\them}.

Then, six months ago, I learned that \cEtruriaKing{\Monarch} \cEtruriaKing{} of Etruria and \cScythiaKing{\Monarch} \cScythiaKing{} of Scythia had arranged a marriage between \cBride{} and the Etruscan crown \cGroom{\prince} \cGroom{}, in order to fulfill an ancient prophecy and prevent civil war. Immediately, I could sense \cBride{}'s mental state deteriorating, though \cBride{\they} hid the distress well from the rest of the world. I too began to dread this wedding, partially out of envy, more because of my concern for \cBride{\them}.

I know only a few ways to help \cBride{\them} now. I fear \cBride{\they} will turn back to alcohol, and so I must remove undue temptation from \cBride{\their} path. Upper-class weddings always come paired with loathsome revelries, festivities where noblemen can lose themselves to drunkenness and lose quite a bit of money gambling in the process. While I have always found these gatherings distasteful-- it pains me to see nobles, normally so elegant and composed, debase themselves-- I haven't stepped in. This time, though, I must be a spoilsport, for I won't let their carrying-on risk \cBride{}'s sobriety. In the case that I fail, I have brought in the ingredients for the remedy I slipped \cBride{\them} last time, but, as it is not a guaranteed cure, I would prefer to avoid a relapse in the first place.

These are small ways to help \cBride{}, and I worry that I cannot even do this much, once \cBride{\they} is married and moves to Etruria with \cGroom{}, who is a few years older. Once \cBride{\they} goes, I know I will never be happy again. Thus, for months now, I have dreamed of running away with \cBride{} and eloping. I haven't gone through with this foolish notion-- I suspect \cBride{\their} disappearance would hinder Scythian political affairs, and, more importantly, I don't even know how \cBride{} feels about me. But if this wedding threatens \cBride{\their} health and sanity too greatly, I will confess my feelings for \cBride{\them}. I'll ask \cBride{\them} to break off \cBride{\their} engagement with \cGroom{} and perhaps consider me instead, though I am naught but a steward. 

I wonder what other surprises will be lurking on this island. While I've never heard of Cos before, I remember the name ``Acheron'' from those horrific Soulblade chants inflicted on me as a child. The word ``ghost'' was always close by. Those two words have resurfaced in my dreams, and I intend to investigate any signs of the paranormal.

Moreover, I've recently received a message from the Soulblades, sent to anyone who's ever studied with them. It warns that the Blackguards, their ancient, anti-magic rivals, intend to strike once more; given the timing of their reemergence, they are likely aiming at this very wedding. As the Blackguards were long renowned as skilled assassins, \cBride{}'s life might very well be at risk, and I want to defend \cBride{\them}. Yet, as a Soulblade, I may be a target as well. Thus, I should engage in magical activities quietly and try to avoid the Blackguards' notice, for even ex-Soulblades may incur their wrath.

If all goes fairly well, \cBride{} and \cGroom{} shall be married tomorrow. If all goes perfectly, \cBride{} \emph{will} be married - to me. But should the Blackguards strike \cBride{\them} down, we may still have our ``happy ever after,'' if not in this world, then in the next . . .
\begin{itemz}[Notes]
  \item You have brought a bag of brown sugar required for the alcoholism remedy. It's currently in your trunk.
  \end{itemz}

\begin{itemz}[Goals]
 \item Win \cBride{}'s heart and \cBride{\their} hand in marriage
 \item Make sure \cBride{} stays safe, and protect \cBride{\them} from alcoholism
 \item Shut down all debauchery, especially Bluffmaster parties
 \item Investigate and disrupt any Blackguard activity
 \item Explore Cos' connections to Soul Magic
 \item Serve the monarchs of Scythia
\end{itemz}

\begin{contacts}
\contact{\cBride{}} the crown \cBride{\prince} of Scythia, whom you adore with all your heart.
\contact{\cScythiaKing{}} \cScythiaKing{\Monarch} of Scythia, a kind-hearted \cScythiaKing{\human}.
\contact{\cScythiaQueen{}} \cScythiaQueen{\Monarch} of Scythia. \cScythiaQueen{\They} showed you some kindness after you left the Soulblades, and was the one who hired you as a steward.
\contact{\cWard{}} \cScythiaKing{} and \cScythiaQueen{}'s adopted child. You know little about \cWard{\them}, and \cWard{\they}'s always seemed like an outsider within the palace.
\end{contacts} 



\end{document}
