\documentclass[char]{Kos}
\begin{document}
\name{\cEmeraldQueen{}}

	Note: You are a capricious NPC ghost. You must help \cAnarchist{} and \cButler{} complete ghost-related research plots. Otherwise, you should not assist any particular character or cause, except for the express purpose of accomplishing one of your goals.
	Three hundred years ago, you were Smaragdos, the first queen of a nation called Scythia, stalwart enemy of another nation called Etruria . . . But that was long ago. You died on this godforsaken island, doing something you don't remember for some purpose you no longer care about, and you became a ghost. After countless decades bound to Cos, you don't remember much of anything from your life beforehand.
	 Post-death, only a few people have ever visited you on this island. There were the architects who came here at some point to refurbish the old castle here. There's the rich guests who have rented out the buildings for a day at a time, hosting fancy events. There's the cleaning crews who scour the place afterwards. But nobody ever stays for any period of time. They always flee too soon, leaving you lonely and bored.
	 Something interesting happened today, at least. A cleaning crew came, along with a self-important official from an eastern country called Assyria that you vaguely recall, and naturally you started eavesdropping on them. They said there would be a royal wedding, between a Scythian \cBride{\prince} and an Etruscan \cGroom{\prince}! You heard some more snatches of conversation, something about a prophecy. One of the cleaning crew was a shifty type-- you liked him especially-- and you saw him trying to conceal a sketchy-looking parcel. You never got to investigate more closely, though, because the official then had some sort of fit. You could immediately tell he was doomed to die within hours, and for a lovely moment you thought you would have a fellow ghost on this island! But alas, the cleaning crew dragged his still-twitching body into their boat and sailed away, and he must have kicked the bucket off at sea somewhere. No new friend for you \ldots
	 But you still have something else to look forward too-- the wedding itself. There'll be drinking and gambling and drama and fortune-telling and more drinking \ldots This is the most interesting thing that's happened to you in decades, and you plan to take full advantage. You've thought up some scenes you'd like to see, and you'll try to set those scenes up today and watch the chaos unfold, so that the lovely memories can sustain you through the years to come.
	 If you're really lucky, maybe you'll finally get another ghost to keep you company.

\begin{itemz}[Goals]
 \item Get someone to die and become a ghost
 \item Watch someone steal or hide an emerald
 \item Watch someone pilfer herbs from the altar
 \item Watch someone lose at least 100 coins in one set of Bluffmaster
 \item Watch someone pass out from drinking alcohol
 \item Watch someone break into the kitchen and tamper with the food
 \item Watch one of the betrothed parties try and back out of the wedding
 \item Watch an argument between two spouses
 \item Watch someone have their fortune told without their consent
  \item Watch someone be successfully waylaid
  \item Watch someone fail to open a lock marked by a golden sigil. You suspect you actually made the sigil lock yourself before dying, but you don't know how or why \ldots
\end{itemz}



\end{document}
