\documentclass[char]{Kos}
\begin{document}
\name{\cFugitive{}}

Fate. Fate was never a myth to you. The winds of prophecy and the distant agonies of your half-forgotten past drive your very existence. For as long as you can remember, you have been able to reach into the currents of legend and mystery and pull forth glimpses of possible futures - you can read the currents of destiny as the strands of the Fates unfurl. Yet sometimes you feel that you know little more than what the spirits whisper to you on the wind - for your own past is a great and terrifying void. When you cast your memory back to your childhood, you can only glean the barest snippets of what your life was like before - the golden contentment of youth, your terror as the cold-eyed kidnappers snatched you from your bed and caged you in a dismal cell far from your home, and a moment of agony so great that your mind refuses to grasp it. The horror of being taken from the safety of your home and imprisoned was enough to break your spirit and shatter your memories. 

You call yourself \cFugitive{}, a wandering fortuneteller, but your own name - your true name - has been lost to you for so long that you fear you would not recognize it if you heard it spoken. And when you gaze within yourself, trying to fill in the missing pieces, things only get worse. There is a great ice-pale hollow where your soul should be. You don't know how you know this, but the same whispering voices of Fate that tell you the fortunes of others on the wind have confirmed it: your immortal soul no longer resides in your body. You are nothing but an empty husk, without a past, without a spirit. But not without a future. When you close your eyes and welcome the oblivion of sleep, the voices of the spirits that guide you still hiss in your ears, offering you hints and snippets of your own destiny. If you seek out the fleeting scraps of memory they have offered you, there is a chance your soul might still be restored to you. And you will not stop until your identity and your strength of will reside within your mortal shell once more.

One thing you do remember, even in the darkness of amnesia. You may not recall exactly what happened to you after you were taken - or even who you were before - but you know, clear as day, who is to blame. It was in the prison oubliettes of \cEtruriaKing{}, the cruel and calculating \cEtruriaKing{\monarch} of Etruria, that your spirit was broken and your mind was tormented. It was \cEtruriaKing{\their} agents that snatched you from your childhood forever, and \cEtruriaKing{\their} cold-hearted soldiers who discarded you like a broken doll when your willpower finally died. And it is \cEtruriaKing{} who brings you here today - you attend the wedding in \cEtruriaKing{\their} retinue, masquerading as an itinerant seer. Your talent for seeing the crystal of truth in the lode of possibility was so great that even the royal bureaucracy could not deny your powers. So you have been brought here, to bring good fortune to the happy couple, and offer the gift of insight to the wedding's other guests. But your presence here is also a chance, at long last, to undermine \cEtruriaKing{\Monarch} \cEtruriaKing{} and all \cEtruriaKing{\their} vicious machinations. If you could, you would take the fiend's life here and now, but you have not the power to strike \cEtruriaKing{\them} down yourself - but perhaps, if you can recall who you once were and the specifics of what befell you, revealing the atrocities \cEtruriaKing{} and \cEtruriaKing{\their} minions inflicted on you will be enough to snatch his authority from beneath \cEtruriaKing{\their} feet.

But your fortuneteller's robes are more than a petty disguise for the sake of revenge alone. The power you possess is real - and you have felt greater and more dire destines moving at the edges of your consciousness. You know, if you can tap into the destinies of enough of the wedding's guests, that this mysterious truth will be revealed to you, prophecy within prophecy. So you will tell fortunes as if you were nothing more than a wandering seer, pandering to one haughty guest after the next, and if you seek out enough of them perhaps the clouds on the horizon will clear and you will understand the greater destiny that awaits the three nations.

Yet the spirits do not only whisper of darkness and vengeance. If your will is strong, and you cling to what hope you have, there is a chance at a happier ending. If the \cEtruriaKing{\human} you hate and the memories you seek await you on this remote island, so too does someone you could love - the voices of fortune, normally so nebulous, are always clear on this point. Someone present on this island is one you might well marry, one who is fated to bring you bliss. Though you have never before traveled to the lonely shores of Cos, the island's name has long resonated through your dreaming mind: for it is here that you will be given a chance at vengeance, a chance at restoration, a chance at prophecy, and a chance at love. All four are within your grasp, if you should only reach out and claim them. 

\begin{itemz}[Goals]
\item Pursue the lost echoes of your memories, and use them to reclaim your missing soul.
\item Use whatever means you can to undermine the authority of \cEtruriaKing{\Monarch} \cEtruriaKing{}.
\item Tell the fortunes of the nobles assembled at the wedding until you are able to discern the greater truth hidden beneath the veil of the future.
\item Find the true love that has been promised to you.
\end{itemz}


\end{document}
