 \documentclass[char]{Kos}
\begin{document}
\name{\cMerchant{}}

Born September 23, in the year 252.

What is worth more - gold, or a king's praise? You don't know for sure. But as long as you can have both, why should you care? As far as you're concerned, most royalty is good for exactly thing: making you richer. You come from a family of Assyrian intellectuals, brilliant men and women who could outthink almost anyone in the fledgling republic. Compared to them, most kings and queens were nothing but inbred dunces. When you first left your childhood home and settled down in Etruria to join a trading company selling luxury goods, you thought you could crack the fledgling market wide open. But the royal family of Etruria - well, offer them enough newfangled opulence, and their coffers might as well be yours. After all, inbred dunces are easy to manipulate. That was the theory, anyways. 

As it turned out, Etruria's present \cEtruriaKing{\monarch}, a cruel and uncompromising tyrant named \cEtruriaKing{}, proved to be anything but an inbred dunce. In fact, you grudgingly admitted, \cEtruriaKing{\they} was nothing short of brilliant. And, though you soon struck up a brisk business with Etruria's citizens - who could, you earnestly believed, use a little bit of luxury in their lives - you never could persuade \cEtruriaKing{} and the royal court to invest in your products. Before now, your only contact with the royal treasury has been... less official, to say the least. When your branch of the business was at risk of going belly-up, you finagled an ``interest-free loan of indefinite duration'' from in your contacts the Etruscan coffers. Was this dubiously legal? Yes. Would you be severely punished if the authorities ever found out? Yes (imprisoned for life, as you recall). Did it work? Yes. So when you heard the news of a royal wedding, you jumped at the chance to secure some noble patronage. Etruscan, Scythian, it really didn't matter - just make one big sale, and you would be set for a long, long time.

Your \cAnarchist{\sibling} \cAnarchist{} confounded your plans, though. Twice as brilliant as you ever were on your best days, it always seemed that \cAnarchist{\they} solved every problem that got in \cAnarchist{\their} way. You tried to tell yourself you weren't jealous, that you could be as smart as \cAnarchist{\they} was. If you could just get \cAnarchist{\them} on your side, whatever projects you embarked upon would be a rousing success. But \cAnarchist{\they} threw a wrench in things. \cAnarchist{\they}'d always proved as stodgy as \cAnarchist{\they} was brilliant, always sticking \cAnarchist{\their} nose into musty tombs and worn-out tomes while you watched the money roll in. Truth be told, though, it was \cAnarchist{\their} scholarly expertise that drove you into business. You always wanted to be an astronomer - when you gazed into the sky, you saw universes laid out before you. But it was \cAnarchist{} who aced every test, remembered every constellation, traced the path of every planet. Galled by your inability to match \cAnarchist{\their} skill, you plunged into more practical fields of work instead. You sometimes wonder, if it weren't for \cAnarchist{}, if you wouldn't have chosen the scholar's path yourself - but that's all irrelevant now. By the time you left, \cAnarchist{\they} was headed straight for a tenured professorship at a prestigious Assyrian university, and dedicated \cAnarchist{\them}self to research. Waste of a good mind, you always told \cAnarchist{\them}.

Your last conversation was not a happy one. \cAnarchist{\They} accused you of caring about nothing more important than profit, and insinuated that you were little better than a common peasant. Stung, you put on an arrogant facade and walked away - but, deep down, you worry that you've lost your \cAnarchist{\sibling}'s respect forever. And then you discovered that \cAnarchist{\they}'d be attending the royal wedding. It was your best chance to see \cAnarchist{\them} again. Perhaps it can even be something more than that: perhaps it's an opportunity for you to prove yourself to \cAnarchist{\them}, to show \cAnarchist{\them} that you're worthy of \cAnarchist{\their} admiration, to finally impress the imperturbable \cAnarchist{}.

So, driven by both profit and \cMerchant{\sibling}ly pride, you graciously accepted your invitation to the royal wedding, held on the distant (and politically neutral) isle of Cos. You packed up a valise (shame they wouldn't let you bring three) full of your most innovative and fascinating wares, including a lavish gift for the happy couple (a cinnamon-flavored distillation of a rare vintage mead imported from Iberia, packaged in filigreed gold). But your most important offering is a unique piece of history, tailored to the desires of all the Sabine royalty. 

Ever since you were a child in Assyria, you'd heard rumours of an ancient artefact known only as the Diadem, a magical token of royalty that was lost when the Sabine empire crumbled. Wouldn't it be a wonderful achievement if you managed to uncover the Diadem and parade your discovery before the assembled royals? Sadly, the real Diadem was lost to history. So you persuaded your best employees - a talented crew of artificers - to make you the next best thing. They acquired an ornate diadem from the correct historical era, then painstakingly enchanted it to give special powers to every royal of Sabine descent who would be attending the wedding, Etruscan and Scythian alike. If your detractors knew, they might call it a ``fake,'' but you prefer to think of it as a work of art in its own right.

Unfortunately, you're not the only merchant attending the festivities. An old rival of yours, a Scythian arms dealer named \cArmsDealer{}, has managed to worm \cArmsDealer{\their} way into \cScythiaKing{\Monarch} \cScythiaKing{}'s retinue. Every time you attend a trade summit or Assyrian bazaar, you find yourself seated across the table from \cArmsDealer{\them} in a game of Bluffmaster - you're certain the \cArmsDealer{\human} cheats, because you recall losing to \cArmsDealer{\them} as often as you won. This simply will not do. Clean \cArmsDealer{} out at the gambling tables and show \cArmsDealer{\them} up for the greedy \cArmsDealer{\InsultOne} that \cArmsDealer{\they} is. 

You're familiar enough with this \cArmsDealer{\InsultTwo} of a \cArmsDealer{\human} to know that, where \cArmsDealer{\they} travels, conflict is never far behind. This is, to put it bluntly, bad news. Nobody buys luxury goods in the middle of a war - austerity measures are the worst - so, if \cArmsDealer{} manages to push the two nations into direct conflict, you're out of luck. What's worse, it seems like they might not even need \cArmsDealer{}'s warmongering to push them over the brink. Oh, the two kings are reasonable enough in their own right - \cScythiaKing{} of Scythia's a kindly old \cScythiaKing{\human}, so obsessed with preserving life that \cScythiaKing{\they}'d never spark a war on \cScythiaKing{\their} own initiative, and \cEtruriaKing{} of course is too cunning to act rashly. But rumour has it that the border clashes between the two nations have been escalating. 

What's even worse, one of your contacts in \cScythiaKing{\Monarch} \cScythiaKing{}'s court has reported that Etruria managed to plant a spy right under \cScythiaKing{\their} nose, feeding information straight to \cEtruriaKing{}. Perhaps if you can figure out who the spy is and reveal their identity to the Scythian monarch, you can defuse some of \cEtruriaKing{}'s leverage on the proceedings, ingratiate yourself with the Scythians, and push for a peaceful resolution.

In addition, you've put together a contingency plan of sorts. Your sources have managed to locate one of the most talented thieves in any of the Sabine states, a daring rogue who goes by the name of \cBurglar{}, and break \cBurglar{\them} out of the Assyrian jail \cBurglar{\they} was languishing in. You reached out to \cBurglar{\them} anonymously, got \cBurglar{\them} admitted to the wedding under the guise of a Scythian fortuneteller, and commissioned \cBurglar{\them} to stage a daring heist. But \cBurglar{\they}'s not going to be robbing \cArmsDealer{} - \cBurglar{\they}'s going to be robbing you. Little does \cBurglar{\they} know that all of your goods (especially the Diadem) have been magically warded and trapped by your artificers. Anyone who touches them will be knocked unconscious. That's when you'll arrive on the scene, discover the ``treacherous thief,'' and pin the crime on \cArmsDealer{} - who, everyone knows, is notoriously underhanded in \cArmsDealer{\their} own right. With the value of your wares reinforced by the attempted theft, and Fresi hopelessly discredited, you hope to steer the two nations away from war and towards something infinitely better - mutual profit.

\begin{itemz}[Notes]
  \item As part of the etiquette of presenting your gift to the happy couple, you should ask them to try the liquor immediately. Do not be offended if they reject your offer, though; they may decide quite reasonably that they should limit their alcohol consumption at this rather tense occasion.
\end{itemz}


\begin{itemz}[Goals]
\item Discredit that bloodthirsty \cArmsDealer{\InsultThree} \cArmsDealer{} by framing \cArmsDealer{\them} for the theft of the Diadem.
\item Make sure a war doesn't break out between Scythia and Etruria.
\item Sell your Diadem to one of the nations present for a sum of at least 1.5 million.
\item Root out the person who's been spying on the Scythian court.
\item Prove your mental superiority by annihilating \cArmsDealer{} at Bluffmaster.
\end{itemz}

\begin{contacts}
\contact{\cAnarchist{}} Your \cAnarchist{\sibling}, a brilliant astronomer and your longtime rival.
\contact{\cScythiaQueen{}} The puritanical and austere \cScythiaQueen{\monarch} of Scythia.
\contact{\cEtruriaKing{}} The Etruscan \cEtruriaKing{\monarch}, a cunning ruler and potential customer.
\contact{\cArmsDealer{}} A greedy arms dealer and old enemy of yours.
\contact{\cBurglar{}} A burglar you've hired to steal your Diadem, enabling you to pin the crime on \cArmsDealer{}.
\end{contacts}


\end{document}
