\documentclass[char]{Kos}
\begin{document}
\name{\cScythiaQueen{}}

\updatemacro{\cFugitive}{
  \nickname{Thoesi}
  \mapnickinformal
}

Born April 3, in the year 256.

You went into \cFugitive{\their} room. \cFugitive{\Their} stuffed bear still smiled on her pillow, and \cFugitive{\their} yellow robe was still folded on her dresser. Only \cFugitive{\they}-- \cFugitive{}, your ten-year-old  \cFugitive{\offspring}-- was missing.

It was your fault, \cScythiaKing{}, your \cScythiaKing{\spouse} and the \cScythiaKing{\monarch} of Scythia, raged. You had refused to forgive Etruria for sacking and burning Achillea, the border town where you had spent some vacations as a child. Back then, before you married \cScythiaKing{}, you were only a minor noble, not famous at all, so the Etruscans likely didn't know how attached you were to Achillea and its townspeople. They may not have meant the attack to be personal, but it wounded you nonetheless. Secretly thirsting for revenge, you decided a few months later to go after Hero, an Etruscan border town of the same size as Achillea. Scythian intelligence warned you that Cerintha, the queen of Etruria, had considered visiting Hero "for charitable purposes," but you signed off on the strike nonetheless. 

Cerintha had indeed arrived at Hero by the time of the attack, and she was caught up in the battle and inadvertently killed. And, in the tradition of violence that has bound your two lands for so long, Etruria cruelly retaliated, abducting Scythia's crown \cFugitive{\prince}, \cFugitive{}, from her own palace bedroom. You knew full well what would happen next-- the ice-hearted \cEtruriaKing{\Monarch} of Etruria would have her killed, perhaps in secret, or perhaps at a grisly public execution, as punishment for Cerintha's death.

There was no public execution, but, in the next few days, your land's Soulblade doctors searched for your \cFugitive{\offspring}'s soul and found it was no longer among the living. All of Scythia mourned for the lost child, yet you were isolated in your sorrow, for you were crushed by a guilt that you could admit to no one, not even your \cScythiaKing{\spouse}. \cScythiaKing{They} stopped talking to you and moved out of your bedroom, while you turned your back on the world and wept day and night. But someone reached out to you before you went quite mad with grief . . . Memnon, then the greatest doctor among the Soulblades. He came to you in a dream and revealed that he practiced not only healing, but certain illegal arts besides. He offered to call on the black magic that had first won the Soulblades their fame, and he swore that you would speak with your \cFugitive{\offspring} once more. And your broken mind believed him.

He demanded money for ``rare, arcane ingredients,'' and he fed you drugs to ``open your mind.'' Looking back, you recognize it was all dangerous quackery, but you were under his thrall, your sanity crumbling as you drank potion after potion. You saw zigzagging black shapes everywhere and heard sounds that weren't there, malicious, ghostly whispers that pursued you through nightmares and clung to you even when you awoke. You tottered, half in reality, half in a world of imagined evils. Countless voices all pressed upon you-- but never the one voice you craved.

Finally, your \cScythiaKing{\spouse} came back to you. \cScythiaKing{\They} perceived easily that you were in trouble that went beyond mere grief, but you asked \cScythiaKing{\them} not to pry. \cScythiaKing{\They} complied and embraced you gently, and his warmth gave you the strength to break free from Memnon's influence. You stormed into the Soulblades' quarters and summoned the wicked ''doctor'' before you, and he came, quivering, sputtering that you would be ''vulnerable to the spirits'' if you left him now. But you had had enough. You threw him into prison and had his research confiscated. Furthermore, you had all the Soulblades searched, and you discovered that they had all sorts of horrors packed away-- boxes of human bones, bottles stuffed with blood, hearts and lungs, chests and chests of dried poppies. They whined that they used the items only for official medical work, that they studied the tissues to treat diseases and used the poppies only to relieve the pain of the dying. On the other hand, you were positive Memnon wasn't the only Soulblade who practiced black magic in defiance of Scythian law. Eventually, you imprisoned the most flagrant transgressors and slashed state funding for Soulblade research, though you couldn't shut down the whole lot-- their legitimate medical research is too valuable for that. But you and the Soulblades are no longer on good terms. You avoid their healing as much as you practically can, and you have realized that their cultish necromancy is useless at best and madness-inducing at worst.

When you finally recovered from Memnon's abuse, you turned your thoughts back to Achillea. One of the only survivors of Etruria's attack was a four-year-old \cWard{\kid}, \cWard{}, the only surviving member of a noble family you had stayed with as a child. \cWard{\Their} entire family and estate had been wiped out by the Etruscans, and you pitied \cWard{\them}. Still grieving for your own child, you and your \cScythiaKing{\spouse} decided to become \cWard{}'s official guardian. Though you never adopted him into the official line of succession, \cWard{\they} is still an honorary \cWard{\prince}, with the title, the room in the palace, the generous funding available whenever \cWard{\they} shows need, and all the other accouterments of royalty. You and \cScythiaKing{} had little direct involvement, since the child was cared for mainly by tutors and nurses, so you simply watched with horror as \cWard{} grew first into a bratty kid and then into a wretch of a teenager, a thoughtless rake who is utterly ungrateful towards you and your \cScythiaKing{\spouse}. First, \cWard{\they} joined up with the Soulblades to study healing, just to spite you. Then, this past year, \cWard{\they} went off to the Assyrian school-city Nineveh to ''study,'' but you heard rumors that \cWard{\they} was doing the exact opposite. Worst of all, you've seen the bills! \cWard{\They}'s been hosting drunken parties, gambling away \cWard{\their} state-provided stipend . . . It's a miracle \cWard{\they} hasn't gone bankrupt or quite flunked out yet! Now, you're perfectly well aware that young people often hold their own festivities at a wedding-- complete with disgusting alcohol and reckless gaming-- and you're sure \cWard{}, as the sibling of the betrothed, will be heading the debauchery this time around, humiliating Scythia's royal family, and perhaps causing further catastrophes. You've made up your mind to squash all such troublemaking. This is one wedding that can do without it.

Ah, this wedding. You can't believe that, in the end, Etruria may steal both your children. You know that a wedding between a top-ranking noble from Scythia and another from Etruria is needed to keep the peace, but do you really want peace? No, you want revenge-- for your dead \cFugitive{\offspring}, for Achillea, for the generations of Scythians terrorized by Etruscan evil. 

The time for peace is over, and Scythia and Etruria should finally enter the war they've tiptoed around for centuries. Scythian intelligence suggests that the \cEtruriaKing{\monarch} of Etruria has had similar thoughts and is considering attacking Scythia. Regardless of whether the rumors are true, you want to go on the offensive against Etruria, invading them and conquering them once and for all, and your military leaders have drawn up plans to do so. However, your \cScythiaKing{\spouse} has so far refused to order the attack, because \cScythiaKing{\they} wants to first talk with \cEtruriaKing{}, Etruria's \cEtruriaKing{\monarch}, at the wedding. \cScythiaKing{\They} claims that \cScythiaKing{\they} simply wants to prevent \cEtruriaKing{} from preparing Etruria for the war, and indeed you would like catch Etruria off-guard with your attack. However, you suspect \cScythiaKing{} has another reason for the delay-- \cScythiaKing{\they}'s too soft-hearted to finally commit Scythia to the war predicted by the prophecy. \cScythiaKing{\They}'d rather preserve the peaceful status quo; that's why \cScythiaKing{\they} arranged the wedding in the first place. Your ever-practical \cBride{\offspring}, \cBride{}, has quietly voiced \cBride{\their} support for peace, and \cBride{\they} therefore did not complain about being married off to an Etruscan. 

Alas, there's peace-supporters all around. On the Etruscan side, an obnoxious merchant named \cMerchant{} has been quite vocal in \cMerchant{\their} dovishness, as war would no doubt interfere with \cMerchant{\their} profits. You can't entirely avoid that haggling snake, sadly, since according to rumors \cMerchant{\they} has dug up the ancient Diadem! You and your \cScythiaKing{\spouse} have got to get the Diadem back into Scythia's possession, or else be forever condemned by history. You've already met with the treasurer and figured out the maximum price Scythia can pay \cMerchant{} for that artifact-- it's no doubt much higher than anything that dirt-cheap Etruria will offer. Hopefully, that transaction will be over quickly-- you've only met \cMerchant{} a few times, yet you really can't stand \cMerchant{\them}. Then there's the Assyrian peacemakers, who are explicitly dedicated to preventing war and thwarting your aims; Sirasu Noon, the Assyrian secretary of international relations, will likely be the greatest threat among them.

The main supporter of war, as far as you know, is \cArmsDealer{}, a Scythian weapons dealer. Of course, \cArmsDealer{\their} opponents would say \cArmsDealer{\they}'s also motivated by \cArmsDealer{\their} pocketbook, but you know \cArmsDealer{}'s hatred for Etruria is sincere-- much of \cArmsDealer{\their} family was wiped out at the battle of Achillea. Furthermore, you both find \cMerchant{} distasteful, and have traded quite a few stories about \cMerchant{\their} oily politicking.. You feel quite close to \cArmsDealer{} as a result. 

Between the two of you, you'll stop these peacemakers from persuading your \cScythiaKing{\spouse} to refrain from attacking Etruria, for you want nothing less than war. Ideally, you'll somehow prevent Etruria from preparing from war and convince \cScythiaKing{} to order the attack, though you doubt things will turn out quite so perfectly. In the worst case, you could just order the attack yourself, though that would be a serious betrayal of \cScythiaKing{}'s trust.

Of course, there's the dreaded possibility that peace will prevail, and the wedding will go on. You've got one decent option in this case-- you must simply marry off your troublesome ward instead of your own child. Switching out the betrothed this close to the wedding is unorthodox, to be sure, but there's no obvious reason for Etruria to object. Moreover, you've got an increasingly tempting reason to send \cWard{\them} away,  beyond the fact that you can't stand the fool. Just before leaving for Cos, you overheard your ladies-in-waiting gossiping about Musa, \cWard{}'s late mother, and \cScythiaKing{}! Now, when you pressed your servants for more information, they immediately fell silent, but the suspicions have been planted in your mind. You want to trust your \cScythiaKing{\spouse}, and \cScythiaKing{\they}'s innocent, in all likelihood. But if \cScythiaKing{} has indeed betrayed your marriage vows for that Musa, \cScythiaKing{\they}'ll suffer your full wrath, for the only things you hate more than sexual impurity are gambling, alcohol and Etruria. You'll observe \cScythiaKing{\their} interactions with \cWard{} and, if you observe any undue fondness, openly confront your \cScythiaKing{\spouse}; if your worst fears are confirmed, then you'll send \cScythiaKing{}'s precious bastard packing to gloomy Etruria and make the lives of both \cScythiaKing{\parent} and \cWard{\offspring} hell. And you might just order up a war to finish things off\ldots


\begin{itemz}[Goals]
\item Destroy Etruria through war
\item Save \cBride{} from this marriage by sacrificing \cWard{} instead
\item Oppose all Soul Magic
\item Learn whether \cWard{} is really \cScythiaKing{}'s child; if so, take revenge
\item Shut down gambling, drinking, and all related debauchery
\end{itemz}

\begin{contacts}
\contact{\cScythiaKing{}} Your \cScythiaKing{\spouse}, whom you hope has been loyal to you.
\contact{\cBride{}} Your angel of a child, who must be rescued from this vile wedding.
\contact{\cArmsDealer{}} Your companion in anti-Etruria sentiment.
\contact{\cButler{}} The young steward of the Scythian palace. \cButler{\They} is Memnon's only child, but for some reason \cButler{\they} is now as anti-Soulblade as you-- you checked with divination magic when \cButler{\they} was first hired as a lowly palace server. \cButler{\They} has since advanced rapidly thanks to \cButler{\their} admirable work ethic; you've also put in a good word with \cButler{\their} supervisors.
\contact{\cWard{}} Your intolerable brat of a ward.
\end{contacts}

\end{document}
