\documentclass[blue]{Kos}
\begin{document}
\name{\bBlackguards{}}

You are a Blackguard - one of the last remaining members of a hidden order of assassins that has endured behind the scenes for generations. Although the Scythian branch of your order was purged by the vicious zeal of the upstart Soulblades, the Blackguards remain a powerful force in the affairs of both Etruria and Assyria. Rather than submitting themselves to the fickle whims of magic, the Blackguards put their faith only in their own, human abilities. Highly trained in the arts of stealth, deception, and covert killing, they are assassins without equal, and some of the feats they perform would seem like magic to the untrained eye. Not all of these skills are murderous in nature--– for example, to improve your ability to mislead others, fledgling Blackguards spend long hours practicing the game of Bluffmaster, and many become quite skilled. Blackguards are traditionally indoctrinated from a young age, growing from children into fully fledged assassins over the course of decades. After they completing several years of rigorous training, acolytes are initiated as “Half-Blackguards; a few take on the burden of extra missions and training to become full Blackguards. Given the deadly nature of their work, Blackguards are supposed to abide by a rigid code of honor, which states that incurring  collateral damage  while carrying out a mission is the worst possible shame. 

The Etruscan Blackguards, led by the mysterious Full Blackguard known only as the White Rose, serve the Etruscan royal family with a grudging loyalty. This is a great humiliation, to serve at the beck and call of an arrogant monarch who barely even knows they exist, much less what they are truly capable of. Despite this humiliation, they hold as strictly to tradition as possible, and obey the commands the White Rose gives without question. The Assyrian half of the order, on the other hand, generally take a looser approach to tradition. Ever since the collapse of the Sabine empire, the Assyrian have become something of a loose cannon, lurking in the shadows, assassinating targets to serve their own inscrutable purposes. Their order lacks the rigid hierarchy of the Etruscan Blackguards, and an Assyrian Blackguard may be far more unpredictable than their Etruscan counterpart. 

Blackguards prefer poisoning and subterfuge to unsubtle combat and possess several esoteric means of administering venom. The most notable of these are their ability to infuse textiles, food, and ordinary sewing needles with doses of poison, allowing them to use these mundane objects to incapacitate or kill. If someone trained in the manufacture of poison observes a poisoned object closely, they may be able to discern its deadly nature. Blue poison enervates its victims, sapping their strength and making them less effective fighters; pink poison instead knocks its victims unconscious. The Soulblades are able to concoct potent remedies for these poisons, but you must thwart their meddling. Fortunately, if you knock a Soulblade out, they cannot attempt Soul Magic rituals for twenty minutes after they wake up. If you see any suspicious Soulblade activity, you should endeavor to halt it immediately - their brand of magic is too dangerous to be allowed in Sabine lands.

The secret symbol of the Blackguard order is the rose, and the Blackguards attending the royal wedding have arranged to leave any covert messages by the bouquet of roses. Blackguards traditionally use a simple cipher to communicate, disguised as the gibberish of a Soulblade incantation: only every third letter of the message, beginning with the first letter, should be read.  Traditional Blackguards have a strict agenda: 

\begin{itemize}
\item Avoid collateral damage while assassinating your targets.
\item Keep your identities secret, even from one another.
\item Keep all Blackguard technologies hidden from the common rabble.
\item Shut down Soulblade magic if at all possible.
\end{itemize}


\end{document}
