\documentclass[blue]{Kos}
\begin{document}
\name{\bErrata{}}

\begin{itemize}
\item Game starts on June 13, 300 (i.e. 300 years after the Sabine empire split up), three hours and fifty minutes before sunset begins.
\item Weddings are supposed to be peaceful events. Weapons and other items whose primary purpose is to injure people seem rather out-of-place.
\item Truthing magic cannot force you to tell the truth. It can, however, retroactively determine how reliable one of your prior statements was.
\item Cos is an Assyrian island, maintained entirely by Assyrian staff.
\item The second boat from Assyria carried \cPoet{} and \cWard{}, who are currently studying in Assyria, as well as the peacemakers \cAnarchist{} and \cArchaeologist{}.
\item Alcohol cannot be drugged, poisoned, or otherwise tampered with.
\item Items of significant historical import are governed by strange laws. If such an object is long-lost and then suddenly rediscovered, the "finder" gains possession of it; if the finder was searching for the object on behalf of a company, then the company is considered the "finder." Only a country-- or countries-- can take over possession of such an item, should the finder choose to give it up. Such a transaction must be sealed with a magical contract.
\item Fortune-tellers are generally royals; it is somewhat surprising to have two commoner fortune-tellers at a royal wedding.
\item "Royal" and "noble" are interchangeable terms, referring to descendants of the original Sabine imperial family.
\item Interrupting someone who is stealing money from a Bluffmaster pot stops them from taking further money; it does not cause them to return anything they have already stolen.
\end{itemize}


\end{document}
