\documentclass[blue]{Kos}
\begin{document}
\name{\bSoulblades{}}

	Rumors abound concerning the Soulblades of Scythia. Some are convinced that you are benevolent healers, dedicated to the well-being of the common people. Others believe that your order is a necromantic cult, obsessed with raising the dead and murderous at heart. As a Soulblade yourself, you know that the truth lies somewhere in between. Soulblade magic has no inherent moral weight – even the simplest incantation can be used for either good or evil. Nevertheless, the Soulblades pretend to be nothing more than an order of healers to reassure the Scythian court of their harmlessness. 

The majority of Soulblade training now focuses on healing potions and simple blessings. There are darker and more arcane schools of Soulblade magic, however, though they are no longer openly taught. A Soulblade of sufficient power can use his magic to determine whether someone’s soul is still among the living, determine when they were born, communicate with the forgotten dead, or even gain power themselves after entering the afterlife. The more esoteric the magic, the more strange the ingredients it requires: from rare jewels and specific kinds of food to drugs or even human body parts, though the most macabre of these are associated with dark rituals that have been forbidden in Scythia for generations. 

One thing you know for certain: the magic of the Soulblades is volatile, and even the simplest ritual can create a disruptive and dangerous psychic backlash. To have even a gambler’s chance at succeeding, a Soulblade must be either incredibly intelligent and highly trained, or possess incredible reserves of innate power. 

Your order’s oldest enemies are the legendary assassins known as the Blackguards, who feared your mystical power and sought to wipe you out. Identified by the sign of the rose, they were a dangerous force in the old Sabine empire. Though the Soulblades managed to wipe the Scythian Blackguards out, it is still whispered that their order persists in Etruria and Assyria. They discovered that stopping Soulblade magic is annoyingly simple: if you are knocked unconscious for any reason, you cannot perform a Soulblade ritual for twenty minutes upon waking.

Nor are the Blackguards your only foes. \cScythiaQueen{\Monarch} \cScythiaQueen{} loathes every Soulblade \cScythiaQueen{\they} comes across, and will stop at nothing to shut you down. \cScythiaQueen{\They}’s out for blood. Rumor has it that \cScythiaQueen{\they} once had close ties to a man named Memnon, one of the most powerful Soulblades ever to walk Scythian soil, before the two fell out. When \cScythiaQueen{\they} broke faith with Memnon, the Soulblades all suffered: the \cScythiaQueen{\monarch} raided the Soulblade quarter in the Scythian capital, uncovering a stash of forbidden materials and moldering corpses. The most talented Soulblades, including Memnon himself, were either imprisoned or exiled, and \cScythiaQueen{} remains a real threat to your order.



\end{document}
