\documentclass[blue]{Kos}
\begin{document}
\name{\bThoesi{}}

Born June 2, in the year 275.

It has all returned to you. The glory of your birthright, the horror of your kidnapping and interrogation, the cold grasp of the spirits as they snatched away your soul. You are more than a penniless wanderer, more than a mere common seer - yes, in your veins flows the blood of kings. You are Thoesi Agathos, the daughter of \cScythiaKing{\Monarch} \cScythiaKing{} and \cScythiaQueen{\Monarch} \cScythiaQueen{} of Scythia, and your soul once again gleams within you like an orb of pure crystal. You remember your father’s caring laugh, your mother's regal pride, and the love they never failed to share with you. You remember gilded curtains, trinkets of bronze and silver, the scent of myrrh in the Soulblades' braziers and the songs of the troubadours who graced your parent's court. But you also remember the worry that furrowed your parents' brows and etched wrinkles into their skin, the hard-edged conversations they held when they thought you weren't listening. 

And you remember the night it was all stolen from you. Brutal men with cruel eyes and cold voices dragged you from your chambers, binding your hands and sailing off from a hidden cove. They moved silently, almost gracefully, their tabards adorned with roses. At first they pretended to be kind, simpering at you with false smiles as you languished in a locked room of cold granite. \cEtruriaKing{\Monarch} \cEtruriaKing{}, that relentless bastard, took the time to interrogate you \cEtruriaKing{\them}self, prying every secret from your mind with \cEtruriaKing{\their} imperious gaze. Try as you might, you could conceal nothing from \cEtruriaKing{\them} - no lie escaped \cEtruriaKing{\their} notice. And you remember the day \cEtruriaKing{\they} turned to \cEtruriaKing{\their} attendants and said simply, ``I have no more use for the prisoner. Send it away.'' And that they did, sending you to a prison where you were beaten within an inch of your life, the pain so great that your soul slipped from your tenuous grasp and into the void. You remember the years you spent discarded in some forgotten cage, fending off the rats and scorpions for the paltry scraps of food they tossed you. Somehow, you survived. Somehow, you broke free. And now, you’re so close at last to being home again, to being free again, but first you want your revenge on the Etruscan scum who did this to you. They will know how it feels to be lost. They will know how it feels to be broken. And they will never hurt you again.

Make the Etruscans, especially \cEtruriaKing{}, pay for what they did to you. Let your family know that you're alive, and get them to aid you in your revenge. And keep your \cBride{\sibling} - your dear, dear lost \cBride{\sibling} - from marrying that Etruscan lout!

\begin{contacts}
\contact{\cBride{}} Your \cBride{\sibling}, whom you remember as a brilliantly intelligent child, now a gorgeous young \cBride{\human}.
\contact{\cScythiaKing{}} Your \cScythiaKing{\parent}, a good \cScythiaKing{\human} and a good \cScythiaKing{\monarch}.
\contact{\cScythiaQueen{}} Your \cScythiaQueen{\parent}, a kind and caring \cScythiaQueen{\human}.
\contact{\cEtruriaKing{}} Your greatest adversary, a brutal, murderous, ruthless piece of subhuman slime. Also the \cEtruriaKing{\monarch} of Etruria.
\end{contacts} 

Your psychic health max is now 5. You are at full psychic health.

\end{document}
