\documentclass[blue]{Kos}
\begin{document}
\name{\bWhosWho{}}

\emph{These are the commoners and nobles attending the wedding of \cGroom{\Prince} \cGroom{} of Etruria and \cBride{\Prince} \cBride{} of Scythia. They arrived at the island of Cos on six different vessels. Scythia and Etruria each sent two ships, one bearing commoners and the other royals. The first ship sailing from Assyria was populated by servants who would prepare the villa for the ceremony, as well as the diplomat Sirasu - the second carried the rest of the Assyrian delegation as well as \cWard{} and \cPoet{}, who are currently studying in Assyria.)}

\emph{Commoners:}

\cButler{} is the young steward of the Scythian court, tasked with ensuring that the wedding festivities go off without a hitch. The ascension of one so green to such a prestigious position is unprecedented in a Sabine court. It is rumored that \cButler{\they} carries ties to the Scythian order of Soulblades and their esoteric magic.

\cBurglar{} is a fortuneteller traveling with the Scythian delegation, a young \cBurglar{\human} with the gift of insight chosen by the Scythian court to bless the happy couple. As the royal seers are chosen based solely on their talent for the art of divination, the \cBurglar{\human} carries neither lands nor title, and \cBurglar{\they} is a curiosity among the guests for both \cBurglar{\their} unknown heritage and for the fortunes \cBurglar{\they} will reveal to them.

\cArmsDealer{} is an arms dealer whose status as the wealthiest commoner in Scythia got \cArmsDealer{\them} invited to the royal wedding as a ``representative of the commoners.'' A cunning merchant whose services and products go without exception to the highest bidder, \cArmsDealer{\their} military innovations have nevertheless proved effective - perhaps chillingly so - at securing Scythia's borders against barbarians.

\cAssassin{} is the chief steward of the Etruscan court, an elderly but dedicated attendant who has served the crown for decades without fail or complaint. Not a detail passes before \cAssassin{\their} eyes that \cAssassin{\they} does not sign off on, and with \cAssassin{\them} in charge of the royal wedding, it will take a miracle to derail the Etruscan arrangements.

\cFugitive{} is a mysterious fortuneteller accompanying the Etruscan party, a no-name plucked from the ranks of Etruria's commoners to share \cFugitive{\their} prophetic knack with the gathered nobles. \cFugitive{\Their} very talent for divination magic is an astonishment, however - fortunetelling blood traditionally runs in noble veins, and for a mere itinerant to prove the most talented diviner in all of Etruria is either a startling revelation, an unlikely stroke of luck, or a cunning hoax. Particularly surprising is the fact that two commoners, \cFugitive{} and \cBurglar{}, are serving as diviners for the wedding.

\cMerchant{} is a luxury goods merchant, salesman par excellence, and the wealthiest of Etruria's small merchant class. \cMerchant{\They} are the ``ambassador of the common people'' at this wedding, though as a rich Assyrian immigrant \cMerchant{\they} little resembles the average citizen of that impoverished nation. 

\cAnarchist{} is a well-respected Assyrian professor of astronomy and the \cAnarchist{\sibling} of \cMerchant{}, chosen to support the diplomat Sirasu in his peacekeeping efforts.

Sirasu Noon is a renowned Assyrian lawyer, diplomat, master Bluffmaster player, and brilliant political theorist. His scholar's eye, talent for objective assessment, and incisive mind enable him to resolve nearly any conflict - whether it's a territorial dispute, an academic debate, or a blood feud about to erupt in violence, Sirasu is the one who dials down the tensions and makes even the most entrenched opponents see reason.

\cArchaeologist{} is a young but distinguished Assyrian archaeologist, also chosen to support Sirasu as a peacekeeper.

\emph{Royals (From Eldest to Youngest):}

\cEtruriaKing{} is the \cEtruriaKing{\monarch} of Etruria, an icy and brilliant \cEtruriaKing{\human} whose intellect is matched only by \cEtruriaKing{\their} capacity for ruthlessness. The scion of an upstart dynasty that came to power when \cEtruriaKing{\their} father Hyperion overthrew the old Etruscan queen in a bloody coup, \cEtruriaKing{\they} cares about one thing and one thing only: increasing the power of Etruria by any means necessary. No matter who you are, \cEtruriaKing{\they} is not a \cEtruriaKing{\human} to be trifled with.

\cScythiaKing{} is the well-loved \cScythiaKing{\monarch} of the Scythians. Ever since the kidnapping and death of \cScythiaKing{\their} daughter Thoesi, it's been rumored that \cScythiaKing{\they} blames \cScythiaKing{\them}self for every life lost to the senseless feud between the two nations.

\cScythiaQueen{} is the \cScythiaQueen{\monarch} of Scythia and the \cScythiaQueen{\spouse} of \cScythiaKing{}. \cScythiaQueen{\They} is a stalwart believer in propriety, chastity, and temperance as the true pillars of Scythian virtue. After the death of \cScythiaQueen{\their} \cFugitive{\offspring} at Etruscan hands, \cScythiaQueen{} has made no secret of \cScythiaQueen{\their} desire for vengeance, and is also known for \cScythiaQueen{\their} grudge against the mystical Soulblades.

\cGroom{} is the eldest child of \cEtruriaKing{\Monarch} \cEtruriaKing{} and the deceased Queen Cerintha, and the crown \cGroom{\prince} of Etruria. Rather than studying in Assyria like most royals, \cGroom{\they} chose to remain in Etruria, spending several years as an archaeologist studying the ancient capital of the Sabine Empire. Honest and upright, it's said that \cGroom{\they}'ll someday make a competent but boring ruler.

\cBride{} is the only surviving child of \cScythiaKing{} and \cScythiaQueen{}, and heir to the Scythian throne. \cBride{\They} studied law at one of Assyria's finest universities. \cBride{\They} is betrothed to \cGroom{}, the Etruscan crown \cGroom{\prince}, and today's wedding will see the two bound together in sacred matrimony. 

\cPoet{} is the younger \cPoet{\sibling} of \cGroom{\Prince} \cGroom{}, an passionate \cPoet{\prince} loved by the Etruscan people. \cPoet{\They} resembles the late Queen Cerintha in both looks and temperament.

\cWard{} is the adoptive son of \cScythiaKing{} and \cScythiaQueen{}, the child of a noble friend of \cScythiaQueen{}'s who was killed in a border raid by Etruscan troops. \cWard{\They} has not been formally welcomed into the line of succession, and€“ rumor has it \cWard{\they} never got along well with \cWard{\their} adoptive family. \cWard{\They} is now studying something or the other in Assyria, as is customary for young royals.

\end{document}
