\documentclass[white]{Kos}
\begin{document}
\name{\wAssyriaPapers{}}

\emph{(This is an in-game, transferable item. You are magically prevented from signing if you are not the character in question, or if your character does not honestly agree with the statement.)}

Once the requirements below are met, the undersigned bearer of this document (one \cWard{\MYname}) will be allowed to pass through customs and formally enter the Republic of Assyria as a citizen, with all of the rights, privileges, and duties that such status entails. If this document is not completed and certified by all signers, its bearer will not be granted citizenship and any residence in the nation of Assyria must be temporary. All of the below signatures are required for this document to be certified valid.

I, a citizen in good standing of the Republic of Assyria, do hereby certify that the undersigned \cWard{\MYname} is a virtuous and highly productive member of society, and believe that \cWard{\they} ought be allowed to enter the Republic of Assyria as a citizen.

\hrulefill

I, a monarch of the kingdom of Scythia, do hereby certify that the undersigned \cWard{\MYname} is a virtuous and highly productive member of society, and believe that \cWard{\they} ought be allowed to enter the Republic of Assyria as a citizen.

\hrulefill

I, \cWard{\MYname}, do hereby swear by the gods that I am a virtuous and highly productive member of society, and that, if inducted as a citizen of the Republic of Assyria, I will sever all ties of blood and fealty from the nation of my birth and pledge my loyalty to the Assyrian state alone.

\hrulefill

\cWard{\MYname}

\emph{Signatures on this document cannot be erased or forged, and all signatures remain valid even if the signer in question is deceased. The magical dyes used in the drafting of this document cause it to change color (from red to green) when completed. An observer can automatically determine whether or not this document is complete by inspecting it.}

\end{document}

