\documentclass[white]{Kos}
\begin{document}
\name{\wDiademContract{}}

\emph{(This is an in-game, transferable item. You are magically prevented from signing if you are not the character in question, or if your character does not honestly agree with the statement.)}

May it be known: by the joint decree and compact of the ancient Sabine kingdoms, the long-lost Diadem will this day be restored to its rightful homelands. The artifact, a vessel of immense power and royal authority, ought to be protected and enshrined in the treasure vaults of a sovereign nation ? it is far too historic a relic to be allowed to fall into the hands of an individual collector or upstart rebel. Its fate must be decided by the remaining monarchs and authorities of the Sabine nations. For a country to take possession of the Diadem, a monarch of that country (or secretary-level official, in the case of Assyria) must sign this document.

Before signing, the chosen option(s) must be circled. Once the necessary signatures for the chosen option have been obtained, all ink on this document becomes permanent.

The Diadem will enter into the possession of the Kingdom of Scythia.\\
The Diadem will enter into the possession of the Kingdom of Etruria.\\
The Diadem will enter into the possession of the Republic of Assyria.\\
The Diadem will enter into joint possession between two or three of the above nations (circle all that apply).\\

\hrulefill

Monarch of Etruria

\hrulefill

Monarch of Scythia

\hrulefill

Secretary-level Representative of Assyria

\emph{Signatures on this document cannot be forged. Signatures remain valid even if the signer in question is deceased. The magical dyes used in the drafting of this document cause it to change color (from red to green) when completed. An observer can automatically determine whether or not this document is complete by inspecting it.}

\end{document}

