\documentclass[white]{Kos}
\begin{document}
\name{\wEtruriaPapers{}}

\emph{(This is an in-game, transferable item. You are magically prevented from signing if you are not the character in question, or if your character does not honestly agree with the statement.)}

Once the requirements below are met, the undersigned bearer of this document (one \cBurglar{\MYname}) will be allowed to pass through customs and formally enter the sovereign realms of Etruria as a royal subject, with all of the rights, privileges, and duties that such status entails. If this document is not completed and certified by all signers, its bearer will not be granted citizenship and any residence in the kingdom of Etruria must be temporary. This document will be certified valid only when tendered along with the required customs fee.

I, \cBurglar{\MYname}, do hereby swear by the gods that I am a diligent, loyal, and honorable member of society, and that, if accepted as an Etruscan subject, I will sever all ties of blood and fealty from the nation of my birth and pledge my loyalty to the sovereign kingdom of Etruria.

I have also included the required fee for customs and processing of five hundred pieces of gold.

\hrulefill

\cBurglar{\MYname}

\emph{This document will expire on June 15th, in the year 300. Signatures on this document cannot be erased or forged, and all signatures remain valid even if the signer in question is deceased. The magical dyes used in the drafting of this document cause it to change color (from red to green) when completed. An observer can automatically determine whether or not this document is complete by inspecting it.}

\end{document}

