%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%
%Izdubar
\documentclass[greennotebook]{Kos}
\begin{document}

%\item 
%\item 

\startnotebook{\nStrengthInAnarchy{}}

\begin{page}{first}

Every time you look at your hands, your arms, every time you see your face in a mirror, you are disgusted by the frailty of your mortal flesh. Death waits for you in every dawn, waiting to wrap his skeletal fingers around your soul and suck out its seeds like a pomegranate. But this island, at the edge of the Acheron, in the doorway between the realms of gods and men, is different. Here, even death is a temporary affliction. You have seen them, the dead that walk again, intact in soul if not in body. You must learn more. Talk to at least three people about the existence of ghosts on the island. Once you have done so, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

Fools and heretics! They cannot see what you have seen. Their eyes have not been opened. May they all rot before they leave this island! They know so little, the pathetic self-important princes and scholars and salesmen. They cannot help you in your grand design. But there are some who can - those who have been blessed with the wisdom of the parted veil. You have read the secret books of the Soulblades, and you know that the ringing of a bell will compel the spirits of the island to attend you. Find a bell and use it to call a ghost to you. Once you have done so, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Excellent. Perhaps, with the assistance of these specters, you can ensure that your soul survives even when your body finally fails you. Yet even these mysterious ghosts, touched by Thanatos, were once frail and feeble mortals like yourself. Only at the moment of death did they gain the clarity of the gods. Only then were their eyes opened. You must know what this revelation was like. Find out when and how the ghost you summoned died. Once you have done so, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

The presence of ancient queens and spectral powers is a step in the right direction, but the warmth of your blood and the color in your cheeks still separates you from these regal dead. Before your vitality forsakes you, you must find a way to tauten the veil between you and your silent allies - a way to access their power from the mortal realm. The rituals of the Soulblades - those self-destructive fools, playing with Death like a child?s trinket - are a way to touch the living with the fell power of Thanatos. Watch a Soulblade incantation or ritual, then repeat it as best you can far from prying eyes. Once you have done so, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

As the last mystical syllable slips from your mouth, echoing in the empty halls, a cold gust of wind chills you to the bone. As you shiver, acutely aware of your own mortality, you can hear faraway whispers on the breeze. As you wander the island, you realize that the spirits of the dead are no longer silent. Their wisdom is now yours for the taking. Find a GM and get the Ghost Whisperer ability from them. Once you have done so, turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Not all the whispers coursing through your ears are the words of specters. Some seem to come from the soul of the island itself, deep and primordial and full of power. They tell you a simple truth, one which you should have grasped long ago. For your own life force to endure beyond death, another must die forever in your place. One soul for another. A fair trade. Find a fitting sacrifice and kill them. If you have already killed at least one person this game, you need not kill another - the spirits of the island are already satisfied. Once you have done so, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

As your victim?s life ebbs away, you can feel your own soul strengthen. Your heartbeat quickens. You shudder in glee, glutted on the vitality you have consumed, and it takes all your effort to keep from crying out in ecstasy. Yet a great barrier still separates you from the power of death. Why is this? You have paid the price - where is your reward? Give us just a taste, Izdubar, and your prize will be eternity. Over, and over, this mantra in your ears. You must risk your own soul in the darkness of insanity before you can achieve the ultimate victory. Find a way to reduce yourself to a Psychic Health of 0. Once you have done so, turn to page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

You have seen the other side. The touch of Thanatos is cool and smooth as a funereal urn, fingers of pale ceramic, a voice of flax and obsidian. He took your hand and welcomed you as an equal to his realm. He has only sent you back to exact your vengeance on all the fools who doubted you. When your mortal form is at last destroyed, your life will have barely begun - your spirit will endure for eons. Even kings must die, but you will haunt this world forever. Your Psychic Health increases by 2, to a maximum of 7.

\end{page}

\endnotebook

\end{document}
