%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%
%Prymnesios
\documentclass[greennotebook]{Kos}
\begin{document}

\startnotebook{\nButler{}}

\begin{page}{first}

This island is fascinating. The water of the Acheron thrums with power, and every wave that has ever fallen on the jagged stones of Cos has imbued the place with primeval magic. Ordinarily you would want nothing to do with such baleful power, but these are stressful times. Perhaps you can tap into the island'Äôs magic but first you must discover more about it. The assorted royals, merchants, and attendants wandering the island know all sorts of things - you should ask them if they know anything about the history of Cos. Once you have talked to three different people about the island, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

It turns out none of the tidbits of history you could glean from the island'Äôs guests were nearly as valuable as your own nascent Soulblade power. The longer you spend on the island, the more you learn about its true nature. You need only sift the sands of its shores through your fingers to sense the death magic that courses within them, more potent than even the reckless spells of the Soulblades. The Soulblades taught you that the act of ringing a bell had the power to weaken the boundaries between life and death. Perhaps it's just a petty superstition - perhaps not. Find a bell and ring it until you summon a creature that is not human. Once you have done so, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Gods protect you. The island of Cos is not completely in the mortal realm. The souls of the dead still wander here, bound to the land by some ancient power. You have seen them yourself - the bell you rang called one to you, and to your astonishment you found you could understand it when it spoke to you. These wraiths are a reflection of the island'Äôs magic - and perhaps they hold the key to accessing that fell power. You must learn more. Speak with a ghost at length about the island, and learn their name. Once you have done so, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

You'Äôre now certain that this forsaken isle has power - as do you. Already your heart beats in time with the tides of the Acheron, and your veins course with the whispers of the damned. But this magic will not be easy to draw out. You would flee from it if you could - but if worst comes to worst, and \cBride{} needs your help, calling on the island'Äôs mysteries could be your only option. You know now what you must do - blur the boundaries between the living and the dead, by touching the souls of those who are in between. Perform a Soulblade ritual of your choice, while three other people, including two who are sick of soul, stand within 1 ZOC of you. For the rest of game, you can find out other people's psychic health scores at will; you should ask players for their characters' psychic health scores out-of-game. Once you have done so, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Your head hurts. The whispers of generations flood into your mind, and only the meditations the Soulblades taught you as a child help you to keep your sanity. And as you begin to listen to the invisible voices in your ears, you realize that they are speaking words of wisdom, of birth and death and the path Man walks in-between. You may turn to page \nbref{sixth}. 

You now have the power to determine the date at which an individual was born, or the date on which they died. To do so, you must perform a Soulblade ritual with a Risk of 12. It requires no ingredients. The incantation \emph{''ÄúKirolema tachem mesu iulima eya chelma''Äù} will determine an individual's birthdate, and the incantation \emph{''Dauthea kerrim emathu grimmos chalma''} will allow you to determine whether the soul is among the living or among the dead. Once you have finished one of these rituals, find a GM and specify the name of an individual whose birth or death you would like to verify. If you do not know their real name, a well-known pseudonym will also work. Once you use this mechanic, it is consumed and cannot be used again. 

\end{page}

\begin{page}{sixth}

As the susurrus of spirit-voices continues to hiss, one rises above the others, the ragged voice of a half-mad prophet from ages past. There is more power here, it says. But first the stones must be satisfied. The others murmur in agreement, chorusing their desire for fresh mortal souls. The river of death has run too dry for too long. To placate the bloodthirsty spirits, find a dead body and consecrate it by uttering a Soulblade incantation of your choice, allowing the island to taste the sweet oblivion of the moment of their death. Once you have done so, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Everywhere around you are the echoes of the dead. You need only close your eyes to tap into the stream of eternity that ebbs and flows around you. Your own skin grows pale, and you can half-see the souls of those around you roiling beneath their flesh in a tumult of black lightning. The cold fingertips of long-forgotten ghosts press into your spine, your arms, the back of your neck, straining to drag you into the abyss. When you smile, you smile cruelly. So much power. But you may not yet be a strong enough vessel to contain it - all the souls of the island would shatter your mortal form like a flooded river breaching a dam. Find a way to increase your Psychic Health to at least 6. Once you have done so, turn to page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

Your eyes flicker open once more, black as onyx. \cButler{}. What a quaint name. That sad and harrowed little man is but a fraction of who you have become. You are a messenger of the great force called Thanatos, and \cButler{} is but his mortal shell. Every word you speak, every word you hear, echoes itself into oblivion. As long as you stand on the stones of Cos, life and death are but pages in a book, and it is all too trivial to flip between them with a flick of your fingers. But the world must stay balanced, and every life demands a life. Such is the cost of power, and perhaps you will choose to pay it. Turn to page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

You have the power to restore a single dead person to life. However, another must forfeit their life in exchange. To meet this cost, you may sacrifice your own life, or sacrifice the life of another individual. For another to meet the conditions of the sacrifice, they must agree to participate in your ritual by repeating the incantation \emph{''Doros machan eman maran reyden koyome''Äù} You need not inform them that the ritual will kill them. This is a Soul Magic ritual with Risk 12. If it succeeds, your target is restored to life. Their psychic health is equal to 2. The person whose life you have chosen to forfeit immediately dies, regardless of whether you succeed or fail. You can only attempt this ritual once.


\end{page}


\endnotebook

\end{document}
