%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\NEW{Abil}{\aTest}{
%  \s\MYname	{Test Ability}
%  \s\MYtext	{You are a test.}
%  \s\MYeffect	{This is a Test.}
%  }
%
%\NEW{Abil}{\aSpecial}{
%  \s\MYname	{Special Powers}
%  \s\MYtext	{You have special powers, as detailed in your \gTest{}
%		greensheet.}
%  \s\MYeffect	{I have special powers!}
%  \s\MYgreens	{\gTest{}}
%  \suite
%  }
%
%\NEW{Abil}{\aFiremansCarry}{
%  \s\MYname	{Fireman's Carry}
%  \s\MYtext	{You can carry a body as if it were two hands bulky.}
%  \s\MYeffect	{I can carry this body well.}
%  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  
%% Basic DarkWater-style Martial Attack abilities


%% Everyone has these 3
\NEW{Abil}{\aAssist}{
  \s\MYname	{Assist}
  \s\MYtext	{You can assist someone else's attack.  You must be
		within ZoC of both the attacker and target.  Within two
		seconds of an attack, direct this at the attacker,
		saying ``\MYname'' and your CR.}
  \s\MYeffect	{I assist your attack.}
  }
%everyone
\NEW{Abil}{\aKnockOut}{
  \s\MYname	{Knock Out}
  \s\MYtext	{You can knock someone out as an attack. Say your CR.}
  \s\MYeffect	{I knock you out.}
  }

\NEW{Abil}{\aWound}{
  \s\MYname	{Wound}
  \s\MYtext	{You can wound someone as an attack.  This requires an
		{\bf edged} weapon, such as a knife.  Say ``\MYname'' and
		your CR.}
  \s\MYeffect	{I wound you.}
  }


%% the \basecombat macro can be prepended to the Char abils list
%% (in char-LIST.tex)
\def\basecombat{\aKnockOut{}\aWound{}\aAssist{}}

%% only some people have these
\NEW{Abil}{\aDisarm}{
  \s\MYname	{Disarm}
  \s\MYtext	{You can disarm one item from someone as an attack.  Say
		``\MYname'' and your CR.  Point at the item you want to
		disarm.  If the attack works, they must drop that item.}
  \s\MYeffect	{I disarm that item.}
  }

\NEW{Abil}{\aRestrain}{
  \s\MYname	{Restrain}
  \s\MYtext	{You can restrain someone as an attack.  Say ``\MYname''
		and your CR.  You may freely drag, attack, or (if you have
		a weapon) killing-blow them.  To do anything else, or if
		your health state changes, incant ``release'' and let them
		go.}
  \s\MYeffect	{I restrain you.  You are restrained until I incant
		``release.''}
  }
\NEW{Abil}{\aThrow}{
  \s\MYname	{Throw}
  \s\MYtext	{You can throw someone as an attack.  Say ``\MYname'' and
		your CR.  Point in the direction you want to throw them.}
  \s\MYeffect	{I throw you.  Go in the direction I point ten full steps
		or until you hit a wall or similar.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Salo, Maxenes, Meizon, Cryseon, Felix (and possibly Delia and Moenia, if they tell 12+ fortunes)
%Dusty Diadem adds one instance of truthing
\NEW{Abil}{\aTruthingOne}{
  \s\MYname	{Royal Truthing Magic (1x)}
  \s\MYtext	{You can use magic to determine how truthful someone's statement is. Show your target the "Truthing" greensheet for further details.}
  \s\MYeffect	{I observe you and use royal magic to determine your honesty. This is obvious to everyone within sight.}
  }
%Eidola, Hiems
\NEW{Abil}{\aTruthingTwo}{
  \s\MYname	{Royal Truthing Magic (2x)}
  \s\MYtext	{You can use magic to determine how truthful someone's statement is. Show your target the "Truthing" greensheet.}
  \s\MYeffect	{I observe you and use royal magic to determine your honesty. This is obvious to everyone within sight.}
  }
%Paldeen
  \NEW{Abil}{\aTruthingResistanceOne}{
  \s\MYname	{Truthing Resistance (1x)}
  \s\MYtext	{Thanks to years of practice, you have gained an ability that has never before been heard of-- you can resist royal truthing magic. If someone uses the truthing magic mechanic to judge one of your statements, then they will ask you to rate how straightforward and informed your statement is. You can respond to their questioning by giving any ratings that you want. Do not show this card when using this ability.}
  \s\MYeffect	{I resist truthing magic.}
  }
 %Eidola
    \NEW{Abil}{\aTruthingResistanceTwo}{
  \s\MYname	{Truthing Resistance (2x)}
  \s\MYtext	{Thanks to years of practice, you have gained an ability that has never before been heard of-- you can resist royal truthing magic. If someone uses the truthing magic mechanic to judge one of your statements, then they will ask you to rate how straightforward and informed your statement is. You can respond to their questioning by giving any ratings that you want. Do not show this card when using this ability.}
  \s\MYeffect	{I resist truthing magic.}
  }
%Put lots in GM place
   \NEW{Abil}{\aSoulAttack}{
  \s\MYname	{Soul Attack (2x)}
  \s\MYtext	{You use otherworldly energy to attack your target's very soul. This ability can only be used by ghosts and against living targets. You can use this ability 2 times a day.}
  \s\MYeffect	{A black zigzag shots from the floor and strikes you, dealing 1 unit of psychic damage. This ability cannot reduce someone's psychic health below 0.}
  }
  %Put lots in GM place
   \NEW{Abil}{\aRevival}{
  \s\MYname	{Revival (1x)}
  \s\MYtext	{You can resurrect someone other than yourself who died within the last 15 minutes. This ability can only be used by ghosts. You can only cast it once per year.}
  \s\MYeffect	{You are alive and conscious again. Your psychic health max is now 1.}
  }
  %Leda, Izdubar
     \NEW{Abil}{\aKillingBlow}{
  \s\MYname	{Killing Blow (1x)}
  \s\MYtext	{Either through a flurry of well-aimed blows or through strangulation (your choice), you can inflict a killing blow upon an unconscious, willing or paralyzed victim. This mechanic requires a 5-count and is interruptible; you can reuse this ability if interrupted. Your CR must be at least 1 to use this technique.}
  \s\MYeffect	{I physically assault you with deadly force.}
  }
    %Leda, Izdubar, Maxenes, Prymnesios
       \NEW{Abil}{\aTamper}{
  \s\MYname	{Food Tampering}
  \s\MYtext	{You can lace a food item with another chemical (an item numbered between 0016 and 0021). Openly hold the food item in one hand and the chemical in the other hand. Then place the chemical inside the food item's envelope and put a sticker on the outside of the envelope. This is an interruptible mechanic. This mechanic takes 30 seconds if performed in the kitchen and one minute elsewhere. You cannot use this mechanic to steal food from the kitchen}
  \s\MYeffect	{I am lacing this food with another chemical.}
  }
    %Leda, Izdubar
       \NEW{Abil}{\aNeedlePoison}{
  \s\MYname	{Sly Poisoning}
  \s\MYtext	{You can stealthily murder someone by stabbing them precisely with a poisoned\iNeedle{}. First sneak up on them, spending one minute within 1 ZOC of them. Then put a sticker on them, consuming the needle. If you are noticed or interrupted when placing the sticker, the attempt fails; you are caught attempting to stab someone with the needle, but but the needle is not consumed. If the attempt succeeds, tell a GM immediately. Do not show the card when using this ability.}
  \s\MYeffect	{You collapse, dead. This is an acute poisoning effect.}
  }
  %Leda, Izdubar
\NEW{Abil}{\aImprovedWaylay}{
  \s\MYname	{Improved Waylay}
  \s\MYtext	{You can waylay someone in 5-seconds.}
  \s\MYeffect	{I swiftly knock you out.}
  }
  %Salo
\NEW{Abil}{\aFistOfWrath}{
  \s\MYname	{Fist of Wrath (1x)}
  \s\MYtext	{If you whole-heartedly believe someone caused your mother's death, you can inflict a killing blow upon that person, provided they are unconscious, willing or paralyzed. Your CR must be at least 1 to use this ability.}
  \s\MYeffect	{I attack you with deadly force, propelled by vengeful rage.}
  }
  %Eidola, Delia, Leda, Iz and Max
    \NEW{Abil}{\aLockpicking}{
  \s\MYname	{Lockpicking}
  \s\MYtext	{To pick a lock, roll a d20 repeatedly, until the number of 20s that you have rolled equals the lock's Difficulty stat. If you roll two numbers less than three in a row, you make a clumsy, obvious mistake; write "Tampered With" on the lock's sign. This mechanic is interruptible. Only one person can attempt to pick a lock at a time.}
  \s\MYeffect	{I can pick locks.}
  }
  
  %Delia
  \NEW{Abil}{\aImprovedLockpicking}{
  \s\MYname	{Improved Lockpicking}
  \s\MYtext	{When lockpicking, you can treat every lock's Difficulty as 1 point lower.}
  \s\MYeffect	{I am excellent at picking locks.}
  }
  
 %Moenia
\NEW{Abil}{\aSoullessness}{
  \s\MYname	{Soullessness}
  \s\MYtext	{You lack a soul. You do not have a max psychic health and are unaffected by psychic damage.  You believe that you will be hurt by your soulessness after your death. }
  \s\MYeffect	{I am unaffected by psychic damage.}
  }
  

%Paldeen, Fresi, Semiramis
\NEW{Abil}{\aBluffmasterAdd}{
  \s\MYname	{Defensive Technique}
  \s\MYtext	{You can add 3 to any player's sum in Bluffmaster. Initially, you can use this ability once per set. Every time you play three full sets of Bluffmaster, you can use this ability an additional time per set. This ability can be used on yourself.}
  \s\MYeffect	{I add to someone's score}
  }
%all PCs except Meizon and Prym
\NEW{Abil}{\aBluffmasterSubtract}{
  \s\MYname	{Offensive Technique}
  \s\MYtext	{You can subtract 3 from any player's sum in Bluffmaster. Initially, you can use this ability once per set. Every time you play three full sets of Bluffmaster, you can use this ability an additional time per set. This ability can be used on yourself.}
  \s\MYeffect	{I subtract from someone's score.}
}
%Delia, Leda, Max
\NEW{Abil}{\aBluffmasterReroll}{
  \s\MYname	{Chaotic Technique}
  \s\MYtext	{You can force someone to re-roll a die. This ability can be used once per set. This ability can be used on one of your own dice.}
  \s\MYeffect	{I force a die to be re-rolled.}
}

 %Fresi
\NEW{Abil}{\aHack}{
  \s\MYname	{Hacking}
  \s\MYtext	{If you spend two minutes analyzing a communications machine, you can hack it and better understand the effects of the machine's buttons.}
  \s\MYeffect	{I carefully examine a communications machine.}
}
 %Salo
\NEW{Abil}{\aPoetryBonus}{
  \s\MYname	{Poetry Bonus}
  \s\MYtext	{Whenever you roll a D20 to complete a poetry-related task, you can choose to add 5 to your roll.}
  \s\MYeffect	{I write exquisite poetry.}
}
 %Max, Prym, Izdubar, Leda, Semiramis, Felix, Delia, Moenia
\NEW{Abil}{\aFirstAid}{
  \s\MYname	{First Aid (2x)}
  \s\MYtext	{If you spend 1 minute treating someone unconscious, they wake up. If you are interrupted, you must start the minute again. If they fell unconscious because their psychic health score was 0, it now increases to 1.}
  \s\MYeffect	{I apply non-magical healing.}
}
 %Izdubar
\NEW{Abil}{\aChronicPoisoning}{
  \s\MYname	{Chronic Poisoning}
  \s\MYtext	{You feel strangely weak and tired, and your CR is 0 until you get treatment. This is a chronic poisoning effect.}
  \s\MYeffect	{I feel sick.}
}
 %Cryseon, maybe Eidola
\NEW{Abil}{\aAlcoholism}{
  \s\MYname	{Alcoholism}
  \s\MYtext	{If you are offered a drink, you cannot refuse it. Additionally, you must consume at least two drinks every hour. Every time you finish a full hour without consuming two drinks, take two points of psychic damage. Start the first hour when you get this ability.}
  \s\MYeffect	{I am addicted to alcohol.}
}
 %Eidola
\NEW{Abil}{\aAlcoholismBeginning}{
  \s\MYname	{Addictive Tendency}
  \s\MYtext	{If you are offered a drink, you cannot refuse it.}
  \s\MYeffect	{I cannot refuse alcohol.}
}
 %Izdubar, Leda
\NEW{Abil}{\aAcutePoisoningResistance}{
  \s\MYname	{Acute Poisoning Resistance}
  \s\MYtext	{You have built up resistance to poison. You do not notice acute poisoning effects and are completely unharmed by them.}
  \s\MYeffect	{I resist acute poison.}
}
 %lots of copies in GM place
\NEW{Abil}{\aShinyDiademBlessing}{
  \s\MYname	{Blessing}
  \s\MYtext	{Your CR increases by 1 while you are wearing this headdress. You also can choose to add 3 to any poetry-related d20 rolls you make while wearing this headdress.}
  \s\MYeffect	{The shiny headdress makes me stronger.}
}
 %lots of copies in GM place
\NEW{Abil}{\aDustyDiademBlessing}{
  \s\MYname	{Grand Blessing}
  \s\MYtext	{Your CR increases by 2 while you are wearing this. You also gain acute poison resistance-- any acute poisoning effects currently affecting you are ended, and you are unaffected by any effects that start while you are wearing this.}
  \s\MYeffect	{The dusty headdress makes me significantly stronger.}
}
%one for Prym, lots in GM place
\NEW{Abil}{\aWhisperer}{
  \s\MYname	{Whisperer}
  \s\MYtext	{You can see and hear characters wearing solid-colored headbands. If you ever wear a solid-colored headband yourself, you can hand over this ability to one character without a solid-colored headband. Tell them to get a Whisperer card from the K envelope.}
  \s\MYeffect	{I can perceive more than the normal person.}
}
