%%%%%
%%
%% This file sets up the Mem, MemFold, and MemEnvelope datatypes, and
%% creates possible macros for each.
%%
%% The Mem datatype isn't really used directly; it's there so the
%% other datatypes can inherit and share its code.
%%
%%%%%

\DECLARESUBTYPE{Mem}{Element}
\PRESETS{Mem}{
  %% \MYname is the trigger
  \F\MYtext	%%  text
  }


%%%%%
%% MemFold and MemEnvelope are both subtypes of Mem.  MemFold is for
%% fold-n-staple style mempackets, MemEnvelope is for stuff-n-seal
%% style mempackets.  If you want a mempacket to contain interesting
%% contents, like sheets, abilities, and other mempackets, use a
%% MemEnvelope.
\DECLARESUBTYPE{MemFold}{Mem}
\DECLARESUBTYPE{MemEnvelope}{Mem}


%%%%%
%% MemCover and MemPage are for the cover and pages of mempacket
%% booklets, which resemble research notebooks.  These are good
%% substitutes for large piles of MemFolds, and can be useful for
%% things like amnesiac characters.
%%
%% Like MemFolds, MemPages shouldn't directly own any other elements
%% as contents.  Use MemEnvelope instead.
%%
%% MemPages are usually assigned to a MemCover (via \MYmems), with the
%% MemCover representing the entire booklet and assigned to a
%% character.
%%
%% A MemCover is not a mempacket in and of itself; its name is not its
%% trigger and its text is not a memory.
\DECLARESUBTYPE{MemCover}{Mem}
\PRESETS{MemCover}{
  \sd\MYtext	{Each page is a memory/event packet with a separate
		trigger.}
  }

\DECLARESUBTYPE{MemPage}{Mem}


%%%%%
%% \memfold{<trigger>}{<text>}
%% \memenvelope{<trigger>}{<text>}
%% \memcover{<name>}{<pages>}
%% \mempage{<trigger>}{<text>}
%% \startmembook{<name>} <pages> \endmembook
%%
%% These are wrappers around \INSTANCE, useful as 1-shots.
%% \startmembook...\endmembook is a simple wrapper around \memcover
%% that may have better syntax for use within character sheets (inside
%% a \starttag{mems}...\endtag block).
\newinstance{MemFold}{\memfold[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemEnvelope}{\memenvelope[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemCover}{\memcover[2]}{
  \s\MYname{#1}\s\MYmems{#2}}
\newinstance{MemPage}{\mempage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\long\def\startmembook#1#2\endmembook{\memcover{#1}{#2}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{MemFold}{\mTest}{
  \s\MYname	{Test Trigger}
  \s\MYtext	{This is a Test of a fold-n-staple memory packet}
  }
  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Semiramis
\NEW{MemFold}{\mGhostRecognition}{
  \s\MYname	{If you see Character 0016, open this. You may need special abilities for this character to be visible to you.}
  \s\MYtext	{Wow, she looks like Queen Smaragdos herself! You'd recognize those cheekbones anywhere . . .}
}
%Eidola, Max, Cryseon, Meizon
\NEW{MemFold}{\mFugitiveBirthday}{
  \s\MYname	{If you hear about the date "June 2," open this.}
  \s\MYtext	{Huh, that was \cFugitive{}'s birthday.}
}
%Fresi
\NEW{MemFold}{\mFresiExplosives}{
  \s\MYname	{If you see Item 0007, open this.}
  \s\MYtext	{Sugar? Flour? No, this is something far more terrifying - it's one of the bags of experimental explosive stolen from your ship! What could it be doing here?}
}
%Fresi
\NEW{MemFold}{\mFresiPoisonOne}{
  \s\MYname	{If you see Item 0016, open this.}
  \s\MYtext	{This is poison.}
}
%Fresi
\NEW{MemFold}{\mFresiPoisonTwo}{
  \s\MYname	{If you see Item 0019, open this.}
  \s\MYtext	{This is poison.}
}
%Eidola
\NEW{MemFold}{\mAlcoholism}{
  \s\MYname	{Open this the first time you consume alcohol.}
  \s\MYtext	{Alas, you have relapsed into alcoholism. If you are offered a drink, you cannot refuse it. Additionally, you must consume at least two drinks every hour. Every time you finish a full hour without consuming two drinks, take three points of psychic damage.}
}
%Paldeen, Izdubar
\NEW{MemFold}{\mAllergy}{
  \s\MYname	{If you ingest Item 0010, open this.}
  \s\MYtext	{You start coughing uncontrollably. Your throat tightens, and you feel as if your lungs have filled up with fluid. Your CR goes down by 1, to a minimum of 0. These effects last for 5 minutes.}
}
%Hiems
\NEW{MemFold}{\mAchillea}{
  \s\MYname	{Open this if you hear the word "Achillea."}
  \s\MYtext	{Achillea-- that was a pathetic Scythian border town, wasn't it? You recall ordering its destruction for some reason or another, not long before Cerintha's death.}
}
%Leda
\NEW{MemEnvelope}{\mThief}{
  \s\MYname	{Open this when you see the Scythian fortune-teller.}
  \s\MYtext	{Something about this striking young diviner is hauntingly familiar. The lines of \cBurglar{\their} face, the defiant glint in \cBurglar{\their} eyes, \cBurglar{\their} regal poise and \cBurglar{\their} proud voice. You've not seen \cBurglar{\their} like in far too long. Then you remember: your guilty mind conjures up memories of the old Etruscan queen, before King Hyperion dethroned \cBurglar{\them} and left her to die. This diviner is \cBurglar{\their} spitting image! Perhaps \cBurglar{\they} too bears royal blood . . .}
}
%Fresi
\NEW{MemEnvelope}{\mHackEtruria}{
  \s\MYname	{Open this if you successfully hack communication machine 6666.}
  \s\MYtext	{The wiring here is more complex than the devices you're used to, but with a little finagling you're able to reverse-engineer the communicator and figure out what message each button will send. Pressing the button marked ''0'' will launch an all-out attack, pressing the button marked ''1'' will heighten the nation's border defenses, and pressing the button marked ''2'' will spark no additional military activity. Those tricky artificers switched around the classic codes!}
}
%Fresi
\NEW{MemEnvelope}{\mHackScythia}{
  \s\MYname	{Open this if you successfully hack communication machine 7777.}
  \s\MYtext	{The wiring here is more complex than the devices you're used to, but with a little finagling you're able to reverse-engineer the communicator and figure out what message each button will send. Pressing the button marked ''2'' will launch an all-out attack, pressing the button marked ''1'' will heighten the nation's border defenses, and pressing the buttons marked ''0'' or ''4'' will spark no additional military activity.}
}

%Meizon
\NEW{MemCover}{\mSickness}{
  \s\MYname	{Meizon}
  \s\MYmems	{\mSicknessOne{}\mSicknessTwo{}\mSicknessThree{}\mSicknessFour{}}
  }

\NEW{MemPage}{\mSicknessOne}{
  \s\MYname	{Open this 30 minutes into the game, provided you are alive.}
  \s\MYtext	{Your temples throb, and the room spins around you like a child's top. You blink, rubbing your brows, and the sensation fades, save a faint buzzing at the edges of your consciousness. You feel just a fraction colder than you did only minutes ago, but when you touch your forehead your skin is warm and clammy. Perhaps it was something you ate.}
  }

\NEW{MemPage}{\mSicknessTwo}{
  \s\MYname	{Open this packet 1 hour into the game, provided you are alive.}
  \s\MYtext	{The grating whispers in your mind grow louder and harsher, and your brain smolders with sudden pain. Your skin clings to your frame like waterlogged silk, and your hands gnarl and contort into ghastly claws, flickering as you gaze at them. Those around you cannot sense your agony, and you are powerless to tell them, a claustrophobic voice in a silent body. For the next five minutes, you can understand others, but cannot produce any verbal sounds of your own. In addition, your psychic health max decreases by 1.}
}

\NEW{MemPage}{\mSicknessThree}{
  \s\MYname	{Open this packet 2 hours into the game, provided you are alive.}
  \s\MYtext	{Your bones are as hollow as a minstrel's wooden flutes, and every gust of wind plays a dirge within your soul. The slightest touch feels like a thousand rats gnawing at your skin, their mouths stinking of leprous decay. You can feel the blood and pus and bile oozing through your veins, thin and lifeless. When you open your mouth to speak, your tongue is forked like a serpent's, and only a senseless, ceaseless babble emerges. For the next fifteen minutes, you can understand those around you, but you yourself can speak only gibberish. Your psychic health max decreases by 1.}
}

\NEW{MemPage}{\mSicknessFour}{
  \s\MYname	{Open this packet 2 hours and 45 minutes into the game, provided you are alive.}
  \s\MYtext	{Oh gods, oh gods, there is no mercy! The crystal of your soul is cracking into shards, filling your vision with impossible light, setting you adrift on a gray sea beneath gray sails. Every breath you take wraps its hands around your throat and begins to choke you. Tendrils of black lightning crawl beneath your skin, writhing and constricting until you cannot move your limbs. You can feel your heart begin to slow, each beat full of agony. Your psychic health max decreases by 4. If your psychic health max is now below or equal to 0, you die.}
}
%Moenia
\NEW{MemCover}{\mRecoverSoul}{
  \s\MYname	{Moenia}
  \s\MYmems	{\mSoulOne{}\mSoulTwo{}\mSoulThree{}\mSoulFour{}\mSoulFive{}\mSoulSix{}\mSoulSeven{}\mSoulEight{}\mSoulNine{}\mSoulTen{}\mSoulEleven{}\mSoulTwelve{}\mSoulThirteen{}\mSoulFourteen{}\mSoulFifteen{}\mSoulSixteen{}\mSoulSeventeen{}\mSoulEighteen{}\mSoulNineteen{}}
  }

\NEW{MemPage}{\mSoulOne}{
  \s\MYname	{Open this when you are knocked unconscious.}
  \s\MYtext	{This is not the first time you'۪ve felt the savage pain of fists, knocking you back into the dark haze of dream. They wanted to break your spirit, break your will, make you forget you were ever alive. They succeeded: with every blow, the bond between your spirit and your body came undone.}
  }

\NEW{MemPage}{\mSoulTwo}{
  \s\MYname	{Open this when you see a piece of yellow cloth (including character costumes).}
  \s\MYtext	{As you admire the scrap of fabric, you realize that it brings you a sense of calm and contentment you've not felt in years - the soothing peace of childhood, lost in the great void of your memory.}
  }

\NEW{MemPage}{\mSoulThree}{
  \s\MYname	{Open this when you read a message written in another language, or in code.}
  \s\MYtext	{The dead-eyed men and women who snatched you from your home were following the instructions in a letter. When you tried to snatch it from them and read it, it was indecipherable - just like this.}
  }

\NEW{MemPage}{\mSoulFour}{
  \s\MYname	{Open this when you see roses.}
  \s\MYtext	{The ones who abducted you wore simple, practical clothing - adorned with embroidered roses. }
  }

\NEW{MemPage}{\mSoulFive}{
  \s\MYname	{Open this when you see Character 0009 using magic to force others to tell the truth.}
  \s\MYtext	{Even as a child, you were haunted by that cold and calculating gaze. Those eyes, full of flint, smoldering with divination magic, could pry open your soul and make your own tongue betray truths you never wanted to speak.}
  }

\NEW{MemPage}{\mSoulSix}{
  \s\MYname	{Open this when you see someone making a potion.}
  \s\MYtext	{You'۪ve witnessed this strange alchemy before. Concoctions such as these remind you of the desperate pangs of sickness - but also, somehow, of healing. }
  }

\NEW{MemPage}{\mSoulSeven}{
  \s\MYname	{Open this when you hear a message from a ghost.}
  \s\MYtext	{You'۪ve heard the icy whispers of spirits before, long ago. In the midst of trauma, a host of forlorn souls severed your soul from your body. Yet perhaps spirits can be kind as well as cruel - you hope that the spirits of Cos will take pity on you and return your broken soul.}
  }

\NEW{MemPage}{\mSoulEight}{
  \s\MYname	{Open this when you overhear an argument between a parent and their child or stepchild.}
  \s\MYtext	{Heated voices, full of bitter worry and protective love. You'۪ve heard this before. You remember your own parents arguing with you as a child, before you were taken from them.}
  }

\NEW{MemPage}{\mSoulNine}{
  \s\MYname	{Open this when you suffer negative effects due to poison.}
  \s\MYtext	{Your skin crawls and you cannot help but shudder. Tears well in your eyes. It was a poison like this one that finally shattered your will, drove your childish mind half-mad with grief, made your soul vulnerable to the spirits that snatched it away.}
  }

\NEW{MemPage}{\mSoulTen}{
  \s\MYname	{Open this when you physically attack someone.}
  \s\MYtext	{When they came for you, you did not go without a fight. But your small fists could do nothing against those brutal, silent kidnappers, and they laughed pitilessly when you tried to resist.}
  }

\NEW{MemPage}{\mSoulEleven}{
  \s\MYname	{Open this when you see free-flowing water.}
  \s\MYtext	{When the kidnappers took you from your home, you watched the open sea rush by from the narrow window of your cabin. It was the only thing that helped you feel free.}
  }

\NEW{MemPage}{\mSoulTwelve}{
  \s\MYname	{Open this when you eat a brightly-colored fruit.}
  \s\MYtext	{You used to pick fruit like these when you were very young, and you remember their sweet and cloying taste. There are few fruit-trees in Etruria'۪s chilly steppes, outside of the fancy greenhouses the aristocrats frequent.}
  }

\NEW{MemPage}{\mSoulThirteen}{
  \s\MYname	{Open this when you drink alcohol.}
  \s\MYtext	{The harsh fire of the drink unfurls across your tongue like a flower in full bloom, biting and burning in a sudden thrill. You remember this scent, on the breath of someone you loved as a child.}
  }
  
\NEW{MemPage}{\mSoulFourteen}{
  \s\MYname	{Open this when you play a game of Bluffmaster.}
  \s\MYtext	{Games like this were one of your greatest amusements as a child, though you rarely won. Though your main playmate was younger than you, they must have been brilliant - you cherished the few victories you managed to achieve.}
  }  

\NEW{MemPage}{\mSoulFifteen}{
  \s\MYname	{Open this when you see someone picking a lock.}
  \s\MYtext	{Those haunting and evil kidnappers must have picked the lock on your window before snatching you away - you remember hearing a clamor just like this coming from outside. But you mistook it for a stray cat, yowling and scratching at the wall.}
  }

\NEW{MemPage}{\mSoulSixteen}{
  \s\MYname	{Open this when you put on an enchanted headpiece.}
  \s\MYtext	{Your cheeks flush with sudden pride, and your spine straightens. You feel taller and more regal than all those around you: royal blood runs through your veins. In fact, you suspect that you once bore a noble title.}
  }

\NEW{MemPage}{\mSoulSeventeen}{
  \s\MYname	{Open this when you hear a bell ring.}
  \s\MYtext	{When your soul finally slipped away from you into the abyss, the only sounds that echoed in your ears were the serpentine hisses of the spirits and the mournful tolling of distant bells.}
  }

\NEW{MemPage}{\mSoulEighteen}{
  \s\MYname	{Open this when you hold a large quantity of gold (not in the form of money) in your hands.}
  \s\MYtext	{You feel that finery like this is yours by right. Perhaps you lived a life of luxury as a child.}
  }

\NEW{MemPage}{\mSoulNineteen}{
  \s\MYname	{Open this when you have opened at least fifteen pages.}
  \s\MYtext	{You are Thoesi, daughter of \cScythiaKing{\Monarch} \cScythiaKing{} of Scythia. Your memories begin to flicker in your mind once again - but your soul is still lost in the void. You know what you need to do to reclaim it. You must perform a ritual, accompanied by all of your father's children: all the participants must be outdoors, and you must swear to the gods that these are your kin and chant together, \emph{"O spirits, who wandered these forgotten paths, and took my beating heart away from me, return, and give to me the birthright I have lost."} Before you begin the ritual, make sure a GM is present.}
  }
  
\NEW{MemCover}{\mMoeniaFortunes}{
  \s\MYname	{Moenia - Fortunetelling}
  \s\MYmems	{\mMoeniaOne{}\mMoeniaTwo{}\mMoeniaThree{}\mMoeniaFour{}\mMoeniaFive{}\mMoeniaSix{}\mMoeniaSeven{}\mMoeniaEight{}\mMoeniaNine{}\mMoeniaTen{}\mMoeniaEleven{}\mMoeniaTwelve{}\mMoeniaThirteen{}\mMoeniaFourteen{}\mMoeniaFifteen{}\mMoeniaSixteen{}}
  }
  
\NEW{MemPage}{\mMoeniaOne}{
  \s\MYname	{Open this to tell the fortune of character 0001.}
  \s\MYtext	{Your childhood rival has become even more devious than you.}
  }

\NEW{MemPage}{\mMoeniaTwo}{
  \s\MYname	{Open this to tell the fortune of character 0002.}
  \s\MYtext	{One person may marry you to use you. However, there is another person who will make you happier.}
  }
  
\NEW{MemPage}{\mMoeniaThree}{
  \s\MYname	{Open this when you tell the fortune of character 0003.}
  \s\MYtext	{The yellow cloth holds what you seek.}
  }
  
\NEW{MemPage}{\mMoeniaFour}{
  \s\MYname	{Open this when you tell the fortune of character 0004.}
  \s\MYtext	{Tread carefully, for the whims of a fool may have fooled you.}
  }
  
\NEW{MemPage}{\mMoeniaFive}{
  \s\MYname	{Open this when you tell the fortune of character 0005.}
  \s\MYtext	{Do not mistake love for hatred, or adulation for love.}
  }
  
\NEW{MemPage}{\mMoeniaSix}{
  \s\MYname	{Open this when you tell the fortune of character 0006.}
  \s\MYtext	{The one you love has been destroyed by love once before.}
  }
  
\NEW{MemPage}{\mMoeniaSeven}{
  \s\MYname	{Open this when you tell the fortune of character 0008.}
  \s\MYtext	{Your romanceless heart is no sickness, merely a quirk of nature, but the masses will never understand that. If you commit yourself to a wedding nonetheless, the charade will render you miserable.}
  }
  
\NEW{MemPage}{\mMoeniaEight}{
  \s\MYname	{Open this when you tell the fortune of character 0009.}
  \s\MYtext	{The descendant of the dethroned remains alive. If you let them return to Etruria without punishing them properly for their crimes, they and their children will forever threaten your house.}
  }
  
\NEW{MemPage}{\mMoeniaNine}{
  \s\MYname	{Open this when you tell the fortune of character 0010.}
  \s\MYtext	{Your spouse may turn on you, thanks to your own sin.}
  }

\NEW{MemPage}{\mMoeniaTen}{
  \s\MYname	{Open this when you tell the fortune of character 0011. }
  \s\MYtext	{Your oldest rival and your current one are allies, though they may not know it. You should fear their combined power.}
  }

\NEW{MemPage}{\mMoeniaEleven}{
  \s\MYname	{Open this when you tell the fortune of character 0012.}
  \s\MYtext	{You have an unexpected rival in your romance, one who may well have more to offer than you do.}
  }

\NEW{MemPage}{\mMoeniaTwelve}{
  \s\MYname	{Open this when you tell the fortune of character 0013.}
  \s\MYtext	{Watch your back. You are not the only one who would kill for revenge.}
  }

\NEW{MemPage}{\mMoeniaThirteen}{
  \s\MYname	{Open this when you tell the fortune of character 0014.}
  \s\MYtext	{Your adopted sibling needs you desperately.}
  }

\NEW{MemPage}{\mMoeniaFourteen}{
  \s\MYname	{Open this when you tell the fortune of character 0015.}
  \s\MYtext	{You are being used for a plan that'۪s entirely backwards.}
  }

\NEW{MemPage}{\mMoeniaFifteen}{
  \s\MYname	{Open this page once you have told seven or more fortunes.}
  \s\MYtext	{You have a horrifying insight into the Cumaean prophecy. When the prophets of old spoke of a land fighting itself and being bathed in fire, they weren'۪t speaking merely of civil wars and manmade disaster. No, they foretold a catastrophe where nature itself attacked humanity. The land will fight itself through earthquakes, and be bathed in the fire of volcanic wrath!}
  }

\NEW{MemPage}{\mMoeniaSixteen}{
  \s\MYname	{Open this page once you have told twelve or more fortunes.}
  \s\MYtext	{Your magical abilities have matured, and you now carry the gift of insight. Open the packet marked A in game and take one of the abilities within.}
  }

\NEW{MemCover}{\mDeliaFortunes}{
  \s\MYname	{Delia - Fortunetelling}
  \s\MYmems	{\mDeliaOne{}\mDeliaTwo{}\mDeliaThree{}\mDeliaFour{}\mDeliaFive{}\mDeliaSix{}\mDeliaSeven{}\mDeliaEight{}\mDeliaNine{}\mDeliaTen{}\mDeliaEleven{}\mDeliaTwelve{}\mDeliaThirteen{}\mDeliaFourteen{}\mDeliaFifteen{}\mDeliaSixteen{}}
  }
  
\NEW{MemPage}{\mDeliaOne}{
  \s\MYname	{Open this to tell the fortune of character 0001.}
  \s\MYtext	{The one you loathe wants the emeralds to be lost forever.}
  }

\NEW{MemPage}{\mDeliaTwo}{
  \s\MYname	{Open this to tell the fortune of character 0002.}
  \s\MYtext	{Do not let your obsession ruin you. It may yet bring you happiness.}
  }
  
\NEW{MemPage}{\mDeliaThree}{
  \s\MYname	{Open this when you tell the fortune of character 0003.}
  \s\MYtext	{Your rival has plotted on your behalf. Use caution.}
  }
  
\NEW{MemPage}{\mDeliaFour}{
  \s\MYname	{Open this when you tell the fortune of character 0004.}
  \s\MYtext	{Many seek wealth today. None need the money as much as you do.}
  }
  
\NEW{MemPage}{\mDeliaFive}{
  \s\MYname	{Open this when you tell the fortune of character 0005.}
  \s\MYtext	{You are fearful, and your fears are warranted. There is someone near you whom you have not previously feared, but they have long dreamed of ruining you.}
  }
  
\NEW{MemPage}{\mDeliaSix}{
  \s\MYname	{Open this when you tell the fortune of character 0006.}
  \s\MYtext	{Fear the flame that threatens to devour your love.}
  }
  
\NEW{MemPage}{\mDeliaSeven}{
  \s\MYname	{Open this when you tell the fortune of character 0008.}
  \s\MYtext	{You may be destroyed by a drunken decision, though you did not take the drink.}
  }
  
\NEW{MemPage}{\mDeliaEight}{
  \s\MYname	{Open this when you tell the fortune of character 0009.}
  \s\MYtext	{While on this island, you should value poetry, for those who know it can defy death and save three countries from ruin.}
  }
  
\NEW{MemPage}{\mDeliaNine}{
  \s\MYname	{Open this when you tell the fortune of character 0010.}
  \s\MYtext	{You have been betrayed by your child.}
  }

\NEW{MemPage}{\mDeliaTen}{
  \s\MYname	{Open this when you tell the fortune of character 0011. }
  \s\MYtext	{You have feared theft above all, though your very life is in danger.}
  }

\NEW{MemPage}{\mDeliaEleven}{
  \s\MYname	{Open this when you tell the fortune of character 0012.}
  \s\MYtext	{The murderer you want dead is already withering. They may be saved by your poetry.}
  }

\NEW{MemPage}{\mDeliaTwelve}{
  \s\MYname	{Open this when you tell the fortune of character 0013.}
  \s\MYtext	{Do not deny it any longer - your home stinks with sin.}
  }

\NEW{MemPage}{\mDeliaThirteen}{
  \s\MYname	{Open this when you tell the fortune of character 0014.}
  \s\MYtext	{If you watch the alcohol instead of drinking it all yourself, you may arrive at interesting conclusions.}
  }

\NEW{MemPage}{\mDeliaFourteen}{
  \s\MYname	{Open this when you tell the fortune of character 0007.}
  \s\MYtext	{Your soulmate is the youngest person present today.}
  }

\NEW{MemPage}{\mDeliaFifteen}{
  \s\MYname	{Open this page once you have told seven or more fortunes.}
  \s\MYtext	{You have a horrifying insight into the Cumaean prophecy. When the prophets of old spoke of a land fighting itself and being bathed in fire, they weren'۪t speaking merely of civil wars and manmade disaster. No, they foretold a catastrophe where nature itself attacked humanity. The land will fight itself through earthquakes, and be bathed in the fire of volcanic wrath!}
  }

\NEW{MemPage}{\mDeliaSixteen}{
  \s\MYname	{Open this page once you have told twelve or more fortunes.}
  \s\MYtext	{Your magical abilities have matured, and you now carry the gift of insight. Open the packet marked A in game and take one of the abilities within.}
  }
