\documentclass[green]{Kos}
\begin{document}
\name{\gBluffmaster{}}

Bluffmaster is a game of skill, represented out-of-game as a game of chance. It involves gambling, and many great fortunes have been lost and won at a Bluffmaster table.

To play, you and at least two other players must sit down around a triangular table designed for Bluffmaster. To begin a round, every player must put down a minimum bet of 5 gold pieces. All Bluffmaster bets must be written on the Bluffmaster "Pot" sign.

 First, everyone rolls a d20 openly, without using any abilities to manipulate the roll. The person with the highest roll is the "starter." Ties are resolved by re-rolling. Next, everybody rolls a d20; this is your official "Bluffmaster roll" for the round.

Players in a Bluffmaster game act in turn, in clockwise rotation (acting out of turn can negatively affect other players). When it is a player's turn to act, the first verbal declaration or action she takes binds her to her choice of action; this rule prevents a player from changing her action after seeing how other players react to her initial, verbal action.

Until the first bet is made, each player in turn may "check," which means they do not place a bet, or "open," which means they make the first bet. After the first bet, each player may "fold," which means they drop out of the hand and lose any bets they have already made; "call," which means they match the highest bet so far made; or "raise," which means increase the previous high bet. All bets are put into the pot.



\begin{itemz}[Notes]
\item Credit for these rules goes to Wikipedia's "Betting in poker" page.
\end{itemz}

\end{document}