%Cryseon, Meizon
\documentclass[green]{Kos}
\begin{document}
\name{\gScythiaMachine{}}

Etruria owns a pair of extremely valuable military communication machines. You have traveled to Cos with one of these machines, while its counterpart is safely stored at Scythian military headquarters. The counterpart machine at HQ does not have any buttons, so, while you can communicate your intentions to HQ, they cannot send messages back to you. 

Your machine is equipped with three buttons that correspond to three messages for HQ. Exactly one button must be pressed at all times. The machine will send out a magical pulse at the end of sunset to tell HQ which message you've chosen, and then your orders will be promptly executed.

\begin{itemize}
\item 2 = "no escalation in military activity"
\item 1 = "a series of moderate anti-Etruscan activities"
\item 0 = "a multi-pronged, all-out attack on Scythia"
\end{itemize}


You've currently got "2" pressed. "0" will definitely lead to major conflict; "1" may also provoke Scythia and cause war. There may very well be snoops and spies poking around this machine, so, while you've got it stored behind a solid lock in your trunk, you should still keep an eye on it.

NOTE: Traditionally, the "0" button would send a message saying that you want no military activity, while the button with the highest number corresponds to an demand for an all-out attack. However, you don't want snoops deducing your intentions easily, so you've had the numbers swapped.

\end{document}