%Anyone who 
\documentclass[green]{Kos}
\begin{document}
\name{\gGhost{}}

Take this greensheet upon dying if you had a soul at time of death.

You feel this island's strange energy ripping your soul from your body, transforming you into a ghost, and you suddenly have a great many insights into the afterlife. Your corpse disappears, leaving all the items that are still on your person in its place. Put on a solid-colored headband, signifying you are a ghost.

Most living creatures cannot see or hear ghosts, but ghosts can see and hear each other. Ghosts cannot manipulate physical matter or leave this island. However, you can still freely walk around this resort as you did in life; you still cannot pass through solid material or enter locked areas. If you hear the ringing of a bell, you are instinctually compelled to seek out the source of the music. 

Based on your condition at the time of your death, you may have some other special abilities . . . 

- If you had a psychic health score over 0 at the time of your death, you can talk freely, though only ghosts and a few strange living creatures will hear you. Otherwise, you are rendered mute.

- If your psychic health was at least 4 at the time of your death, you can use the Soul Attack ability twice a day. 

- If your psychic health max was 7, you have the special ability of manifesting as a corporeal body for a period of ten minutes every day. In this form, you look as you did in life, and, at the start of the ten minutes, you are neither paralyzed nor unconscious. If you died with a psychic health score of 0, this form has a psychic health score of 1. In every other respect, you look the same and have all the same abilities and statistics as you did at the time of your death. If your physical or psychic state changes while you are in your corporeal form, the ghost form to which you revert is unaffected. You can participate in a marriage ceremony while in this corporeal form.

(Out-of-game note: Please try to be discreet ghosts, to avoid distracting players whose characters cannot see or hear you).
\end{document}