%Cryseon, Meizon
\documentclass[green]{Kos}
\begin{document}
\name{\gScythiaMachine{}}

Scythia owns a pair of extremely valuable military communication machines. You have traveled to Cos with one of these machines, while its counterpart is safely stored at Scythian military headquarters. The counterpart machine at HQ does not have any such buttons, so, while you can communicate your intentions to HQ, they cannot send messages back to you. 

Your machine is equipped with four buttons that could potentially correspond to four possible orders, though you currently have only three courses of action in mind. Exactly one button must be pressed at all time. The machine will send out a magical pulse at sunset to tell HQ which message you've chosen, and then your orders will be promptly executed.

\bf{0 or 3} = no escalation in military activity
\bf{1} = a series of moderate anti-Etruscan activities
\bf{2} = an all-out, multi-pronged attack on Etruria

You've currently got "0" pressed. "2" will definitely lead to major conflict; "1" may also provoke Scythia and cause war. There may very well be snoops and spies poking around this machine, so, while you've got it stored behind a solid lock in \cScythiaQueen{}'s trunk, you should still keep in an eye on it.

NOTE: Traditionally, the "0" button sends a message saying that you want no military activity, while the button with the highest number corresponds to an demand for an all-out attack. However, you currently don't have four different plans, which is why "4" has been coded to equal "0."

\end{document}