\documentclass[green]{Kos}
\begin{document}
\name{\gWedding{}}

A wedding is a solemn ritual, handed down for millennia. For a full minute, the couple must stand together before an altar, while the altar's flame is burning. They must vow to be faithful and to take care of one another; these vows may be composed ahead of time, or spoken ex tempore, from the heart. The wedding must be accompanied by a "witness"-- some friend, relative, mentor, or other person they care about deeply. The two people of honor When they have finished, 

Wedding altars themselves are unusual artifacts, laden with many enchantments. Their flames only burn for the ten minutes while the sun sets on the first day of summer. 

Divorce does not exist. Marriages are ended only by the death of one or both partners.

 betrothed stand in front of an altar and recite vows that they come up with by themselves. The altar is functional for the last seven minutes of game (7 minutes of sunset). One-minute ceremony, at the end of which the altar puts golden circles of light around their hands if the marriage is valid (circles disappear after a few seconds). The one-minute ceremony is interruptible. Invalid marriages: if one or both are under 18, if one or both are unconscious, if the two are close relatives by blood, if one or both is already married to someone else.

This ritual is far more potent than simply siphoning a little piece of a soul. It is also far more dangerous and time consuming. The reward is worth it though. To actually sacrifice a royal soul to the spirits will go a long way toward paying off your debts.

Since this ritual involves the spirits crossing over into this world and devouring the victim's soul from the inside out, the victim will thrash around, and needs to be restrained. Therefore, you need {\bf two} people to help you. If someone (ie: \cAriel{}) wishes to use this ritual to absolve a specific debt, he or she must be one of your helpers.

{\bf To perform the Ritual:}
\begin{description}
\item[First] Knockout or restrain a member of royalty and bring them to the \sRunicCircle{}.
\item[Second] Have your two helpers restrain your victim.
\item [Third] Outline the circle in \iChalk{\MYname}. If the circle is already chalked, you will have to remove the chalk that is present and lay down your own lines.
\item[Fourth] Perform a minute of chanting magical rituals. The person wishing to absolve their debt to you must participate as well. Feel free to use a call and repeat style. The victim will be in intense pain throughout all of this.
\item[Fifth] Killing blow them with a 10 count. This is the only situation in which you may killing blow anyone.
\end{description}

After the killing blow, the victim is dead, and the spirits leave their body. Any of your helpers with debts to you should consider them paid.

\end{document}